---
title: "Analysis"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

#install.packages("pacman")
pacman::p_load(tidyverse, ggbeeswarm, rptR, lme4, magrittr, sjPlot, glmmTMB, lmerTest)

# loading processed data
load("./Data/processed_data.Rdata")
```

#Learning
##Learning Exp1
```{r}
##basic model
learn_model_e1 <- lmer(difference ~ scale(day) + sex + scale(fish_size) + learning + (1 | exp) + (1 | fishID), data = e1) #z-scaling, if you scale fish size you have to scale day as well

summary(learn_model_e1)

tab_model(learn_model_e1) #output table with p-values and random effects
```

##Learning Exp2
```{r}
learn_model_e2 <- lmer(difference ~ scale(day) + sex + scale(fish_size) + learning + exp + (1 | fishID), data = e2)

summary(learn_model_e2)

tab_model(learn_model_e2)
```

##Check Assumptions
```{r}
plot_model(learn_model_e1, type='diag') #all assumptions
plot_model(learn_model_e2, type='diag')

qqnorm(residuals(learn_model_e1)) #linearity of residuals

scatter.smooth(residuals(learn_model_e1)~fitted(learn_model_e1)) #constant variance
```

#Repeatability
##Across Conditions Repeatabilties
```{r Exp 1 Analysis}
#repeatability outputs for across 8 conditions
  
#repetability model function for mixed sexes
rpt_sex <- function(x, y = "") {
  
x <- rpt(difference ~ sex + (1 | fishID), grname = "fishID", data = x, datatype = "Gaussian", nboot = 1000, npermut = 1000, adjusted = FALSE) #estimate of enhanced agree repeatability, differing from adjusted since the fixed effects variance is included in the denominator

assign(y, x, envir = .GlobalEnv) #assigns output to global environment from within function

x
}

rpt_nosex <- function(x, y = "") {
  
x <- rpt(difference ~ 1 + (1 | fishID), grname = "fishID", data = x, datatype = "Gaussian", nboot = 1000, npermut = 1000, adjusted = FALSE)

assign(y, x, envir = .GlobalEnv) #assigns output to global environment from within function

x
}

rpt_sex(e1_reduced, y = "rpt_e1_reduced") #limited baseline period

rpt_nosex(e1_male, y = "rpt_e1_male") #males only

rpt_nosex(e1_female, y = "rpt_e1_female") #females only
```

###R Across Con
```{r}
rpt_sex(e1, y = "rpt_e1") #across conditions rpt model
```

#First half Exp1 Repeatability
```{r, Repeatabiltiy before reverse learning}
e1 %>% filter(day %in% c(1,3,8,10)) -> e1_firsthalf

e1_firsthalf

rpt_sex(e1_firsthalf, y = "rpt_e1_firsthalf") #across conditions rpt model
```

##Single Condition Repeatabilties
```{r repeatabilities in single condition}
#rpt output of all green and also exp2 green

#Reduced baseline
rpt_sex(allgb_reduced, y = "rpt_allgb_reduced")

#Green/Blue Exp 2
rpt_sex(e2gb, y = "rpt_e2gb")

#Green/Blue Exp 2 reduced baseline
rpt_sex(e2gb_reduced, y = "rpt_e2gb_reduced") 

#Green/Blue sexes separated 
rpt_nosex(allgb_male, y = "rpt_allgb_male")
rpt_nosex(allgb_female, y = "rpt_allgb_female")

#Blue/Green Exp 2
rpt_nosex(e2bg, y = "rpt_e2bg")

#Blue/Green sexes separated
rpt_nosex(allbg_male, y = "rpt_allbg_male")
rpt_nosex(allbg_female, y = "rpt_allbg_female")

summary(allbg_male)
count(e1_male, fishID)
count(e1_female, fishID)
```

###R Green/Blue
```{r}
rpt_sex(allgb, y = "rpt_allgb") #all GREBLU
```

###R Blue/Green
```{r}
rpt_sex(allbg, y = "rpt_allbg") #all BLUGRE
```

##Rpt Measurement Sets 
```{r Repeatabilties of Single Conditions Measurement Sets}
#analysis of grouped measurements, first, second, third, all
rpt_set_sex <- function(x, y = "") {
  
x <- rpt(difference ~ set + sex + (1 | fishID), grname = "fishID", data = x, datatype = "Gaussian", nboot = 1000, npermut = 1000)

assign(y, x, envir = .GlobalEnv) #assigns output to global environment from within function

x
}

rpt_set <- function(x, y = "") {
  
x <- rpt(difference ~ set + (1 | fishID), grname = "fishID", data = x, datatype = "Gaussian", nboot = 1000, npermut = 1000)

assign(y, x, envir = .GlobalEnv) #assigns output to global environment from within function

x
}

##rpt of Green/Blue & Blue/Green first measurement set
rpt_set_sex(first, y = "rpt_first")
rpt_set(first_male, y = "rpt_first_male") #males only
rpt_set(first_female, y = "rpt_first_female") #females only

##rpt of Green/Blue & Blue/Green second measurement set
rpt_set_sex(second, y = "rpt_second")
rpt_set(second_male, y = "rpt_second_male")
rpt_set(second_female, y = "rpt_second_female")

##rpt of Green/Blue & Blue/Green second measurement set
rpt_set_sex(third, y = "rpt_third")
rpt_set(third_male, y = "rpt_third_male")
rpt_set(third_female, y = "rpt_third_female")

##rpt of Green/Blue & Blue/Green all three measurement sets
rpt_set_sex(allgbbg, y = "rpt_allgbbg")
rpt_set(allgbbg_male, y = "rpt_allgbbg_male")
rpt_set(allgbbg_female, y = "rpt_allgbbg_female")

##first and second measurements of GREBLU and BLUGRE
rpt_set_sex(first_second_g, y = "rpt_fsg")
rpt_set_sex(first_second_b, y = "rpt_fsb")

##first and third measurements of GREBLU and BLUGR
rpt_set_sex(first_third_g, y = "rpt_ftg")
rpt_set_sex(first_third_b, y = "rpt_ftb")

##second and third measurements of GREBLU and BLUGRE
rpt_set_sex(second_third_g, y = "rpt_stg")
rpt_set_sex(second_third_b, y = "rpt_stb")
```

##Size Removed Rpt
```{r Repeatability models with size removed from DFs}
##running rpt models with size as a factor removed

rpt_sex(allgb_no_size, y = "rpt_e1_no_size")
rpt_sex(allgb_no_size, y = "rpt_gb_no_size")
rpt_sex(e2gb_no_size, y = "rpt_e2gb_no_size")
rpt_sex(allbg_no_size, y = "rpt_bg_no_size")
rpt_sex(e2bg_no_size, y = "rpt_e2bg_no_size")
rpt_sex(first_no_size, y = "rpt_first_no_size")
rpt_sex(second_no_size, y = "rpt_second_no_size")
rpt_sex(third_no_size, y = "rpt_third_no_size")
```


#Colour Preference
##Colour Preference Exp1 Data Wrangling
```{r Colour Preference}
red <- "Red"
gre <- "Green"
gry <- "Grey"
ora <- "Orange"

#making four groups, each share the same colours
group_1 %>% mutate(pref = BASELINE, stim = red) -> df_red_pref  
group_2 %>% mutate(pref = BASELINE, stim = gre) -> df_gre_pref
group_3 %>% mutate(pref = BASELINE, stim = gry) -> df_gry_pref
group_4 %>% mutate(pref = BASELINE, stim = ora) -> df_ora_pref

full_join(df_red_pref, df_gre_pref) -> red_gre #first step to join all col pref DF's

full_join(red_gre, df_gry_pref) -> red_gre_gry #second step

full_join(red_gre_gry, df_ora_pref) -> col_pref #all col prefs together in  DF

col_pref <- mutate_if(col_pref, is.character, as.factor) #changed chr to fctr
```

##LMMs Colour Preference
```{r, colour preference models}
col_pref_LMM <- function(df){
  x <- lmer(BASELINE ~ scale(day) + sex + learning + (1 | fishID), data = df)
}

col_pref_LMM(group_1) -> pref_red_model

tab_model(pref_red_model)

col_pref_LMM(group_2) -> pref_gre_model

tab_model(pref_gre_model)

col_pref_LMM(group_3) -> pref_chk_model

tab_model(pref_chk_model)

col_pref_LMM(group_4) -> pref_ora_model

tab_model(pref_ora_model)
```

##Repeatability of Colour Preference
```{r repeatbiltiy of colour preference}
##rpt for colour preference
rpt_pref <- function(x, y = "") { #function that creates df of time spent in one colour over the other in its condition
  
x <- rpt(BASELINE ~ 1 + (1 | fishID), grname = "fishID", data = x, datatype = "Gaussian", nboot = 1000, npermut = 1000)

assign(y, x, envir = .GlobalEnv) #assigns output to global environment from within function

x
}

rpt_pref(group_1, y = "red_pref") #preference for red colour
rpt_pref(group_2, y = "green_pref") #preference for green colour
rpt_pref(group_3, y = "grey_pref") #preference for check colour
rpt_pref(group_4, y = "orange_pref") #preference for orange colour
 
rpt_pref(group_1_male, y = "red_pref_male")
rpt_pref(group_1_female, y = "red_pref_female")

rpt_pref(group_2_male, y = "green_pref_male")
rpt_pref(group_2_female, y = "green_pref_female")

rpt_pref(group_3_male, y = "check_pref_male")
rpt_pref(group_3_female, y = "check_pref_female")

rpt_pref(group_4_male, y = "orange_pref_male")
rpt_pref(group_4_female, y = "orange_pref_female")

#rpt col pref exp2
rpt_pref(group_exp2, y = "exp2_pref")
```

#Reverse Learning
##Reverse Learning Exp1
```{r reverse learning models}
##models to determine reverse learning in experiment 1
reverse_model_e1 <- lmer(difference ~ learning + scale(day) + relevel(sex, ref = "male") + scale(fish_size) + (1 | exp) + (1 | fishID), data = e1)
summary(reverse_model_e1)

reverse_e1 <- lmer(difference ~ learning + day + relevel(sex, ref = "male") + scale(fish_size) + (1 | exp) + (1 | fishID), data = e1)
summary(reverse_e1)

#reverse_e1_reduced <- lmer(difference ~ learning + I(day-8) + relevel(sex, ref = "male") + scale(fish_size) + (1 | exp) + (1 | fishID), data = e1_reduced)
summary(reverse_e1_reduced)

reverse_e1_reduced <- lmer(difference ~ learning + day + sex + scale(fish_size) + (1 | exp) + (1 | fishID), data = e1_reduced)
summary(reverse_e1_reduced)
```
## LMM Reverse Learning Exp1
```{r}
reverse_e1 <- lmer(difference ~ learning + scale(day) + sex + scale(fish_size) + (1 |exp) + (1 | fishID), data = e1)
summary(reverse_e1)
```

##Reverse learning Exp2
```{r reverse learning in exp2}
e2 %>% filter(learning %in% c("second", "secondreverse")) -> e2_second

reverse_e2_second <- lmer(difference ~ learning + scale(day) + sex + scale(fish_size) + (1 | exp) + (1 | fishID), data = e2_second)
summary(reverse_e2_second)

e2 %>% filter(learning %in% c("third", "thirdreverse")) -> e2_third

reverse_e2_third <- lmer(difference ~ learning + day + sex + scale(fish_size) + exp + (1 | fishID), data = e2_third)
summary(reverse_e2_third)

hist(e2$difference)
reverse_e2 <- lmer(difference ~ set + day + sex + fish_size + (1 | exp) + (1 | fishID), data = e2)
summary(reverse_e2)

reverse_e2_new <- lmer(difference ~ learning + day + sex + scale(fish_size) + (1 | exp) + (1 | fishID), data = e2)
summary(reverse_e2_new)

reverse_e2_reduced <- lmer(difference ~ set + day + (1 | fish_size) + (1 | exp) + (1 | fishID), data = e2_reduced)
summary(reverse_e2_reduced)
```

#Organising Outputs
01##Rpt Outputs
```{r Formatting Repeatabiltiy Outputs} 
#changes number of digits in output to 3
options(digits = 3)

##function for getting vector of results for rpt analysis
rpt_output <- function(w){

w -> x

c(x[[4]][1], x[[5]][1], x[[6]][1:2], x[[7]][1:2]) -> y

z <- data.frame(t(sapply(y,c)))
}

##outcomes as data frames
rpt_output(rpt_e1) -> Across_Conditions

rpt_output(rpt_allgb) -> Green_Blue
rpt_output(rpt_allbg) -> Blue_Green

rpt_output(rpt_first) -> First
rpt_output(rpt_second) -> Second
rpt_output(rpt_third) -> Third

rpt_output(rpt_allgbbg) -> All

rpt_output(red_pref) -> Red
rpt_output(green_pref) -> Green
rpt_output(grey_pref) -> Grey
rpt_output(orange_pref) -> Orange
```

##Renaming Rpt Outputs
```{r}
#function for renaming output variables
rename_output_func <- function(x) {
  
   x %>% rename(R = fishID, lowCI = X2.5., highCI = X97.5.)
}

#function that changes first column named rownames to conditions
rownames_col_to_con <- function(x) {

x <- cbind(conditions = rownames(x), x)

x
}

#funtion that binds outputs together
rename_rm_col <- function(y, z) {

rbind(y) -> x1

rownames(x1) <- z

x1 %>% rownames_col_to_con -> x2

rename_output_func(x2) -> x
}

rename_rm_col(rbind(Across_Conditions, Green_Blue, Blue_Green, First, Second, Third, All), c("Across", "Green_Blue", "Blue_Green", "First", "Second", "Third", "All")) -> rpt_outputs

rename_rm_col(rbind(Red, Green, Grey, Orange), c("Red", "Green", "Grey", "Orange")) -> pref_outputs
```

##Rpt Outputs Sex
```{r rpt outputs in sexes}
## separated sexes
rpt_output(rpt_e1_male) -> Across_Male
rpt_output(rpt_e1_female) -> Across_Female

# all green male and female
rpt_output(rpt_allgb_male) -> GreenBlue_Male
rpt_output(rpt_allgb_female) -> GreenBlue_Female

# all bluemale and female
rpt_output(rpt_allbg_male) -> BlueGreen_Male
rpt_output(rpt_allbg_female) -> BlueGreen_Female

#grouped measurements blue and green
rpt_output(rpt_first_male) -> First_Male
rpt_output(rpt_first_female) -> First_Female

rpt_output(rpt_second_male) -> Second_Male
rpt_output(rpt_second_female) -> Second_Female

rpt_output(rpt_third_male) -> Third_Male
rpt_output(rpt_third_female) -> Third_Female

rpt_output(rpt_allgbbg_male) -> All_Male
rpt_output(rpt_allgbbg_female) -> All_Female

#colour preference male and female
rpt_output(red_pref_male) -> red_pref_male_output
rpt_output(red_pref_female) -> red_pref_female_output

rpt_output(green_pref_male) -> green_pref_male_output
rpt_output(green_pref_female) -> green_pref_female_output

rpt_output(check_pref_male) -> check_pref_male_output
rpt_output(check_pref_female) -> check_pref_female_output

rpt_output(orange_pref_male) -> orange_pref_male_output
rpt_output(orange_pref_female) -> orange_pref_female_output

rename_rm_col(rbind(Across_Male, Across_Female, GreenBlue_Male, GreenBlue_Female, BlueGreen_Male, BlueGreen_Female, First_Male, First_Female, Second_Male, Second_Female, Third_Male, Third_Female, All_Male, All_Female), c("Across_Male", "Across_Female", "Green/Blue_Male", "Green/Blue_Female", "Blue/Green_Male", "Blue/Green_Female", "First_Male", "First_Female", "Second_Male", "Second_Female", "Third_Male", "Third_Female", "All_Male", "All_Female")) -> rpt_outputs_sex #df rpt outputs sex separated

rename_rm_col(rbind(red_pref_male_output, red_pref_female_output, green_pref_male_output, green_pref_female_output, check_pref_male_output, check_pref_female_output, orange_pref_male_output, orange_pref_female_output), c("red_pref_male_output", "red_pref_female_output", "green_pref_male_output", "green_pref_female_output", "grey_pref_male_output", "grey_pref_female_output", "orange_pref_male_output", "orange_pref_female_output")) -> pref_outputs_sex #df pref rpt outputs sex separated


full_join(rpt_outputs, rpt_outputs_sex) -> rpt_outputs_all #repeatability output with original and also sexes split
full_join(pref_outputs, pref_outputs_sex) -> pref_outputs_all
```

##Repeatabiltiy Tables
```{r}
write.table(rpt_outputs, file = "rpt_outputs_table.csv", sep = ",", row.names = FALSE) #exports table to project file

write.table(rpt_outputs_sex, file = "rpt_outputs_sex_table.csv", sep = ",", row.names = FALSE)

write.table(rpt_outputs_all, file = "rpt_outputs_all_table.csv", sep = ",", row.names = FALSE)

write.table(pref_outputs, file = "pref_outputs_table.csv", sep = ",", row.names = FALSE)

write.table(pref_outputs_sex, file = "pref_outputs_sex_table.csv", sep = ",", row.names = FALSE)

write.table(pref_outputs_all, file = "pref_outputs_all_table.csv", sep = ",", row.names = FALSE)
```

#Clear Environment
```{r}
#rm(list = ls(all.names = TRUE))
```


