---
title: "Spare"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

#knitr::opts_knit$set(root.dir = '/Users/dominicmason/OneDrive\ -\ UNSW/hons') #sets WD as project for all chunks - doesn't change directory for setup chunk

#install.packages("pacman")
#install.packages("ggThemeAssist")
#install.packages("ggbeeswarm")
#install.packages("rptR")
#install.packages("lme4")
#install.packages("lmerTest")
#install.packages("wesanderson")
#install.packages("forestplot")
#install.packages("broom")
#install.packages("ggbeeswarm")
#install.packages("ggforce")
#install.packages("cowplot")
#install.packages("gridExtra")
#install.packages("ggpubr")

#install.packages("effects")
#install.packages("sjPlot")
library(effects)
library(sjPlot)


library(ggpubr)
library(gridExtra)

library(cowplot)
library(rptR)
library(lme4)
library(ggplot2)
library(ggforce)
library(ggbeeswarm)

#install.packages("tidyverse")
library(tidyverse)
pacman::p_load(readxl, tidyr, dplyr, magrittr, lubridate, stringr, purrr)

library(lubridate)
library(wesanderson)
#library(broom)
```

FIX PREF OUTPUTS - was issue with taking out bootstraps for altering code

NEED TO WORK OUT HOW TO NAME OBSERVATION AND MERGE DATA FRAMES - COMPLETE

LOOK UP HOW TO GET GOOD AT MAKING FOREST PLOTS - COMPLETE

COMMENT ON ALL CODE - NAME CHUNKS (GROUP CHUNKS ACCORDINGLY) - COMPLETE

CONTINUE SEPARATED SEXES OUTPUTS - COMPLETE

FIX BIND OUTPUT DATA FRAMES CHUNK => FUNCTION NOT WORKING - COMPLETE

##data check experiment 1
```{r data check before merge}
str(e1_data)

e1_data %>% count(marking) -> e1_data_count

e1_data_count 

e1_data %>% group_by(marking) %>% summarise(n=n()) -> e1_data_sum

e1_data_sum

e1_data %>% filter(zone == "CS") %>% group_by(type, marking, test, filepath, date, day, exp, tod, learning, exp_group) %>%
  summarise(time = mean(time_min), arena = unique(arena)) -> e1_fil

e1_fil %>% count(marking) -> e1_fil_count

e1_fil_count

e1_data %>% filter(marking %in% c("a7289", "a7695")) -> dup_data

dup_data %>% filter(zone == "CS") %>% group_by(type, marking, test, filepath, date, day, exp, tod, learning, exp_group) %>%
  summarise(time = mean(time_min), arena = unique(arena)) -> dup_fil_test

dup_data

str(e1)
```
```{r}
# Save an object as a file, ready to import into other rmd document
saveRDS(rpt_outputs, file = "rpt_outputs.rds")
```

##finding missing fish
```{r}
fish_check <- function(x){
e1_data %>% filter(marking == x)
}

fish_check("a7426") -> a7426
fish_check("a7330") -> a7330
fish_check("a7417") -> a7417
fish_check("a7586") -> a7586
fish_check("a7463") -> a7463
fish_check("a7342") -> a7342
fish_check("a7329") -> a7329
fish_check("a7364") -> a7364
fish_check("a7287") -> a7287 #don't think this was a replacment fish unti exp2
fish_check("a1111") -> a1111
fish_check("a7042") -> a7042
fish_check("a7704") -> a7704
fish_check("a7174") -> a7174
fish_check("a7197") -> a7197
fish_check("a7012") -> a7012
fish_check("a7097") -> a7097
fish_check("a7271") -> a7271
fish_check("a7447") -> a7447
fish_check("a7557") -> a7557
fish_check("a7584") -> a7584
fish_check("a7745") -> a7745
fish_check("a8106") -> a8106
```
removed from 01_import 
```{r functions for filtering, eval = FAlSE}
##not working how i want, so eval = F

base6_probe2 <- function (x, y) {
  x %>% filter(unit %in% c("UNIT1", "UNIT2", "UNIT3", "UNIT4", "UNIT5", "UNIT6", "PROBE1", "PROBE2")) %>% 
  group_by(y) %>% #because missing data and e1_data have to be group_by differently
  summarise(time = mean(time_min), arena = unique(arena)) %>%
  add_diff
}

base2_probe2 <- function (x, y = "") {
  x %>% filter(unit %in% c("UNIT5", "UNIT6", "PROBE1", "PROBE2")) %>%
  group_by(y) %>%
  summarise(time = mean(time_min), arena = unique(arena)) %>%
  add_diff
}


base6_probe2(new_missing, c(type, marking, test, day)) -> missing_filter_test
base6_probe2(e1_data, (type, marking, test, filepath, day) -> e1_filter_test
base2_probe2(new_missing, y = type, marking, test, day) -> missing_filter_reduced_test
base2_probe2(e1_data, y = type, marking, test, filepath, day) -> e1_filter_reduced_test
```
#Data Check Exp 2
```{r exp 2 data check}
e2_data %>% group_by(marking) %>% summarise(n=n()) -> e2_data_sum

e2_data_sum
```

#Removed from 01_import
```{r eval = F}
##redundant due to function in 01_import
arrange(allgb, fishID) -> allgb_arranged

allgb_arranged %>% select(-fish_length, -fish_width, -fish_size) -> allgb_no_size

arrange(e2gb, fishID) -> e2gb_arranged

e2gb_arranged %>% select(-fish_length, -fish_width, -fish_size) -> e2gb_no_size

arrange(e1, fishID) -> e1_arranged

e1_arranged %>% select(-fish_length, -fish_width, -fish_size) ->e1_no_size

arrange(allbg, fishID) -> allbg_arranged

allbg_arranged %>% select(-fish_length, -fish_width, -fish_size) -> allbg_no_size

arrange(first, fishID) -> first_arranged

first_arranged %>% select(-fish_length, -fish_width, -fish_size) -> first_no_size

arrange(second, fishID) -> second_arranged

second_arranged %>% select(-fish_length, -fish_width, -fish_size) -> second_no_size

arrange(third, fishID) -> third_arranged

third_arranged %>% select(-fish_length, -fish_width, -fish_size) -> third_no_size
```

#Import Rpt Results
```{r importing rpt results from file}
##must use function in analysis tab rather than this
read.csv("./data/rptcon.csv", header = TRUE) -> rptcon 
read.csv("./data/rptpref.csv", header = TRUE) -> rptpref
```

#Check NAs
```{r check NAs}
sum(is.na(e1$sex)) #checking for NAs in sex variable

sum(is.na(e1$difference)) #checking for NAs in difference variable
```

#Explore Data
```{r check for anomallies}
attach(allexp) #attached df to session
search() #checks what is in the session
str(allexp) #checks structure of df
summary(sex) #gets summary of variable
summary(fishID)
```

#More data checking
```{r eval = FALSE}
attach(allexp)

ufishID <- unique(fishID) #creates list of unique fish IDs
single <- match(ufishID, fishID) #
usex <- sex[single] #creates a list of factors with 2 levels "female" & "male" - where female is 1 and male is 2

data4 <- data.frame(ufishID = test, sex = usex)

summary(data4)
str(data4)
head(data4, n = 20)

detach(allexp)
```

#More Data Check
```{r checking data}
#some fish are ran more then expected...
e1 %>% count(vars = fishID) -> count_e1

count_e1

e1 %>% filter(fishID %in% c("a7289", "a7695")) -> dup_e1

dup_e1

e1 %>% filter(fishID %in% c("a7205", "a7447")) -> test_e1

test_e1

e2 %>% count(fishID)

count_e1

e1 %>% group_by(fishID) %>% summarise(n=n()) -> e1_sum_post_merge

e1_sum_post_merge

e2 %>% group_by(fishID) %>% summarise(n=n()) -> e2_sum_post_merge

e2_sum_post_merge

##checking which exp are NA}
is.na(e1$exp)

which (is.na(e1$exp))

e1 %>% filter(row_number() %in% c(98, 106, 114, 122)) -> exp_NAs

exp_NAs

##checking fish after DFs were merged
fish_check_postmerge <- function(x){
e1 %>% filter(fishID == x)
}

fish_check_postmerge("a7426") -> a7426_postmerge
fish_check_postmerge("a7330") -> a7330_postmerge
fish_check_postmerge("a7417") -> a7417_postmerge
fish_check_postmerge("a7586") -> a7586_postmerge
fish_check_postmerge("a7463") -> a7463_postmerge
fish_check_postmerge("a7342") -> a7342_postmerge
fish_check_postmerge("a7329") -> a7329_postmerge
fish_check_postmerge("a7364") -> a7364_postmerge
fish_check_postmerge("a7287") -> a7287_postmerge #don't think this was a replacment fish unti exp2
fish_check_postmerge("a1111") -> a1111_postmerge
fish_check_postmerge("a7042") -> a7042_postmerge
fish_check_postmerge("a7704") -> a7704_postmerge
fish_check_postmerge("a7174") -> a7174_postmerge
fish_check_postmerge("a7197") -> a7197_postmerge
fish_check_postmerge("a7012") -> a7012_postmerge
fish_check_postmerge("a7097") -> a7097_postmerge
fish_check_postmerge("a7271") -> a7271_postmerge
fish_check_postmerge("a7447") -> a7447_postmerge
fish_check_postmerge("a7557") -> a7557_postmerge
fish_check_postmerge("a7584") -> a7584_postmerge
fish_check_postmerge("a7745") -> a7745_postmerge
fish_check_postmerge("a8106") -> a8106_postmerge
```

```{r}
#third_no_size <- rpt(difference ~ day + (1 | fishID), grname = "fishID", data = third_no_size, datatype = "Gaussian", nboot = 0, npermut = 0)
#third_no_size
```

```{r}
#rpt_outputs <- rbind(all_con, single_gb, single_bg, first_both_single, second_both_single, third_both_single, all_both_single)

#rownames(rpt_outputs) <- c("all_con", "single_gb", "single_bg", "first_both_single", "second_both_single", "third_both_single", "all_both_single") #renames observations

#rpt_outputs %<>% rownames_col_to_con %>% rename_output_func

#rownames(rpt_outputs) #checks observation names
#colnames(rpt_outputs) #checks variable names

#rbind(red_preference, gre_preference, check_preference, orange_preference) %>% rename_output_func -> pref_outputs #binds preference outputs

#rownames(pref_outputs) <- c("red_preference", "gre_preference", "check_preference", "orange_preference") 

#pref_outputs %<>% rownames_col_to_con

#rpt_outputs

#pref_outputs
```

```{r}
#rbind(all_con_male, all_con_female, all_green_male, all_green_female, all_blue_male, all_blue_female, first_male, first_female, second_male, second_female, third_male, third_female, both_con_male, both_con_female) %>% rename_output_func -> rpt_outputs_sex #binds rpt outputs data frames

#rownames(rpt_outputs_sex) <- c("all_con_male", "all_con_female", "all_green_male", "all_green_female", "all_blue_male", "all_blue_female", "first_male", "first_female", "second_male", "second_female", "third_male", "third_female", "both_con_male", "both_con_female") #renames observations

#rpt_outputs_sex %<>% rownames_col_to_con

#rbind(red_pref_male_output, red_pref_female_output, green_pref_male_output, green_pref_female_output, check_pref_male_output, check_pref_female_output, orange_pref_male_output, orange_pref_female_output) %>% rename_output_func -> pref_outputs_sex #binds preference outputs

#rownames(pref_outputs_sex) <- c("red_pref_male_output", "red_pref_female_output", "green_pref_male_output", "green_pref_female_output", "check_pref_male_output", "check_pref_female_output", "orange_pref_male_output", "orange_pref_female_output") 

#pref_outputs_sex %<>% rownames_col_to_con
```

condition	repeatability	SE	    lowCI	highCI	P[LRT]	P[permutation]
across  	0.068	        0.036  	0	    0.103	  0.224	  0.04
green	    0.008	        0.036 	0	    0.106	  0.448	  0.38
blue    	0.152	        0.07    0.028 0.316	  0.00786	0.02
GB1     	0	            0.05   	0	    0.163  	1   	  1
GB2     	0.001	        0.008	  0	    0.026  	1	      0.36
GB3     	0	            0.00   	0	    0.012 	1      	1
allGB   	0.017       	0.026 	0     0.086 	0.266  	0.25

condition	repeatability	SE  	lowCI	highCI	LRT	permutation
red     	0.453	        0.082	0.316	0.608	  1	  0.01
green   	0.471        	0.077	0.339	0.626  	1	  0.01
check   	0.47        	0.067	0.31	0.591	  1	  0.01
orange  	0.475       	0.072	0.309	0.606	  1	  0.01

```{r tod effect}
#checking for effect of time of day
exp1 %>% add_tod -> exp1_tod

model <- lmer(difference ~ updatedsex + day + tod + (1 | fishID), data = exp1_tod)

summary(model)

exp2 %>% add_tod -> exp2_tod

model <- lmer(difference ~ sex + day + tod + (1 | fishID), data = exp2_tod)

summary(model)
```

```{r, Filtering GB Condition}
##unneeded due to above function
#e1_cs %>% filter(exp == "GREBLU") -> e1gb
#e2_cs %>% filter(exp == "GREBLU") -> e2gb
#e1_cs_reduced %>% filter(exp == "GREBLU") -> e1gb_reduced
#e2_cs_reduced %>% filter(exp == "GREBLU") -> e2gb_reduced
```

```{r forest plots in different conditions, eval=FALSE}
#rpt forest plots from extraced and imported file
forest_con <- ggplot(data = rpt_con, aes(x=conditions, y=R)) +
  geom_errorbar(aes(ymin=lowCI, ymax=highCI), width = 0.05, position = position_dodge(0.3)) +
  geom_point(aes(x = conditions, y = R), position = position_dodge(0.3))+
  geom_hline(yintercept = 0, lty = "dotted") +
  labs(x = "condition", y = "repeatability", title = "Repeatabiltiy of Aversive Learning Across Conditions") +
  coord_flip()

forest_con

head(rptcon)
```

```{r forest plots of colour preference,eval=FALSE}
forest_pref <- ggplot(data = rpt_pref, aes(x=conditions, y=R)) +
  geom_errorbar(aes(ymin=lowCI, ymax=highCI), width = 0.05, position = position_dodge(0.3)) +
  geom_point(aes(x = conditions, y = R), position = position_dodge(0.3))+
  geom_hline(yintercept = 0, lty = "dotted") +
  labs(x = "colour", y = "repeatability", title = "Repeatabiltiy of Colour Preference") +
  coord_flip()

forest_pref
```

```{r}
#ggplot(RYYR, aes(exp, time_min, color=marking)) + 
  #geom_quasirandom(dodge.width=0.4, alpha=0.7) +
  #facet_wrap(.~type)
```

```{r}
#rpt_gb <- rpt(difference ~ day + fish_size + (1 | fishID), grname = "fishID", data = allgb, datatype = "Gaussian", nboot = 100, npermut = 100)
#rpt_gb
```

```{r}
forest_rpt_outputs <- ggplot(data = rpt_outputs, aes(x = conditions, y = R)) +
  geom_errorbar(aes(ymin = lowCI, ymax = highCI), width = 0.05, position = position_dodge(0.3)) +
  geom_point(aes(x = conditions, y = R), position = position_dodge(0.3))+
  geom_hline(yintercept = 0, lty = "dotted") +
  labs(x = "condition", y = "repeatability", title = "Repeatabiltiy of Aversive Learning Across Conditions") +
  coord_flip()

forest_rpt_outputs

forest_pref_outputs <- ggplot(data = pref_outputs, aes(x = conditions, y = R)) +
  geom_errorbar(aes(ymin = lowCI, ymax = highCI), width = 0.05, position = position_dodge(0.3)) +
  geom_point(aes(x = conditions, y = R), position = position_dodge(0.3))+
  geom_hline(yintercept = 0, lty = "dotted") +
  labs(x = "condition", y = "repeatability", title = "Repeatabiltiy of Aversive Learning Across Conditions") +
  coord_flip()

forest_pref_outputs
```

```{r}
m1 <- lm(difference ~ sex + tank + exp, data = e1)
summary(m1)
```

```{r Bootstrap Rpt}
plot(rpt_e1, grname = names(rpt_e1$ngroups), scale = c("link",
"original"), type = c("boot", "permut"), main = NULL,
breaks = "FD", xlab = NULL)

print(rpt_e1)
```

```{r}
#geom_hline(aes(yintercept = yintercept, linetype = Lines), line.data)

#geom_hline(aes(yintercept= 10, linetype = "NRW limit"), colour = 'red') +
    #geom_hline(aes(yintercept= 75.5, linetype = "Geochemical atlas limit"), colour= 'blue') +
   # scale_linetype_manual(name = "limit", values = c(2, 2), 
                      #guide = guide_legend(override.aes = list(color = c("blue", "red"))))
  
  #theme(legend.position = "none")
```

```{r}
e1 %>% 
  ggplot(aes(sex, difference, col = sex)) + 
  geom_hline(yintercept = 0, linetype = "dashed", colour = "grey40", size = 0.5) +
  geom_hline(yintercept = 2.695262, colour = "coral1", size = 1.5) +
  geom_hline(yintercept = 5.063168, colour = "cyan1", size = 1.5) +
  geom_quasirandom(dodge.width = 0.6, alpha = 0.5) + 
  theme(
    legend.position = c(.95, .95),
    legend.justification = c("right", "top"),
    legend.box.just = "right",
    legend.margin = margin(6, 6, 6, 6)
    ) +
  labs(col = "Sex") +
  theme(legend.key = element_rect(fill = "white", colour = "grey90"))
```

```{r}
#scale_colour_gradient(values = c((low = "3132B43", high = "#999999"), (low = "#132B43", high = "#009E73"), (low = "132B43", high = "#E69F00"), (low = "#132B43", high = "#D55E00"))) +

#scale_x_discrete(name = "stim", breaks = c("Check", "Green", "Red", "Orange"),labels = c("Check\nGrey", "Green\nBlue", "Red\nYellow", "Orange\nMagenta")) +

#?scale_colour_identity
```

```{r}
##this section was made in an attempt to get a legend for the bottom observations only
#rpt_outputs %>% filter(conditions %in% c("all_con", "single_gb", "single_bg")) -> rpt_outputs_top
#rpt_outputs %>% filter(conditions %in% c("first_both_single", "second_both_single", "third_both_single","all_both_single")) -> rpt_outputs_bot
```

```{r}
figure <- plot_grid(fig1A, fig1B, fig1C,
                    labels = c('A','B','C'),
                    label_x = 0.2,
                    ncol = 1)

figure
```

###Model Selection
```{r learning}
##mAll Subjects Selection
library(leaps)
fit.diff <- regsubsets(difference ~ sex + fish_size + exp + day,
                              data = e1, nbest = 2)
summary(fit.diff)

plot(fit.diff)
```

```{r}
##Information Criteria
ft.diff1 <- lm(difference ~ sex, dat = e1)
ft.diff2 <- lm(difference ~ sex + fish_size, dat = e1) 
ft.diff3 <- lm(difference ~ sex + fish_size + exp, dat = e1)
ft.diff4 <- lm(difference ~ sex + fish_size + exp + day, dat = e1)


c( BIC(ft.diff1), BIC(ft.diff2), BIC(ft.diff3), BIC(ft.diff4) )

c( AIC(ft.diff1), AIC(ft.diff2), AIC(ft.diff3), AIC(ft.diff4) )
```

```{r}
##Stepwise
library(MASS)

fit.int = lm(difference ~ 1, dat = e1)

forward.fit <- stepAIC(fit.int, direction="forward", scope = ~sex + fish_size + exp + day, k = log(nrow(e1)))

forward.fit$anova 
```

```{r}
add_day <- function(x) { #adding day column
x %>% mutate(day = case_when (grepl("2019-06-24", date) ~ "1",
                              grepl("0024-06-19", date) ~ "1",
                    grepl("2019-06-25", date) ~ "2",
                    grepl("2019-06-26", date) ~ "3",
                    grepl("2019-06-27", date) ~ "4",
                    grepl("2019-07-01", date) ~ "5",
                    grepl("2019-07-02", date) ~ "6",
                    grepl("2019-07-03", date) ~ "7",
                    grepl("2019-07-04", date) ~ "8",
                    grepl("2019-07-08", date) ~ "9",
                    grepl("2019-07-09", date) ~ "10",
                    grepl("2019-07-10", date) ~ "11",
                    grepl("2019-07-11", date) ~ "12",
                    grepl("2019-07-15", date) ~ "13",
                    grepl("2019-07-16", date) ~ "14",
                    grepl("2019-07-17", date) ~ "15",
                    grepl("2019-07-18", date) ~ "16"))
}

add_day2 <- function(x) { #adding day column for experiment 2
x %>% mutate(day = case_when (grepl("D1", filepath) ~ "19",
                    grepl("D2", filepath) ~ "20",
                    grepl("D3", filepath) ~ "21",
                    grepl("D4", filepath) ~ "22",
                    grepl("D5", filepath) ~ "23",
                    grepl("D6", filepath) ~ "24",
                    grepl("D7", filepath) ~ "25",
                    grepl("D8", filepath) ~ "26"))
}  
```

```{r}
rpt_day_sex_size_exp <- function(x, y = "") {
  
x <- rpt(difference ~ day + + scale(fish_size) + (1 | exp) + (1 | fishID), grname = "fishID", data = x, datatype = "Gaussian", nboot = 100, npermut = 100)

assign(y, x, envir = .GlobalEnv) #assigns output to global environment from within function

x
}
```

```{r}
rpt_day_size <- function(x, y = "") {
  
x <- rpt(difference ~ day + fish_size + (1 | fishID), grname = "fishID", data = x, datatype = "Gaussian", nboot = 100, npermut = 100)

assign(y, x, envir = .GlobalEnv) #assigns output to global environment from within function

x
}

rpt_day_sex_size <- function(x, y = "") {
  
x <- rpt(difference ~ day + fish_size + sex + (1 | fishID), grname = "fishID", data = x, datatype = "Gaussian", nboot = 100, npermut = 100)

assign(y, x, envir = .GlobalEnv) #assigns output to global environment from within function

x
}
```

#Old Figure 2
```{r}
##forest plot showing r estimate and 95% CI, conditions grouped according to CS+
cols <- c("Across" = "#708090","Green_Blue" = "#009E73", "Blue_Green" = "#56B4E9", "All" = "#008B8B", "Third" = "#20B2AA", "Second" = "#00CED1", "First" = "#AFEEEE")

forest_rpt_outputs <- ggplot(data = rpt_outputs, aes(x = conditions, y = R, colour = conditions)) +
  geom_errorbar(aes(ymin = lowCI, ymax = highCI), width = 0.3, position = position_dodge(0.3), size = 1.1) +
  geom_point(aes(x = conditions, y = R), position = position_dodge(0.3), size = 2.9) +
  geom_hline(yintercept = 0, lty = "dotted") +
  labs(x = "Condition", y = "Repeatability (R)", title = "Repeatabiltiy of Aversive Learning in Different Conditions") +
  facet_col(vars(CS), scales = "free_y", space = "free") + #facet_col produces a better forest plot than facet_wrap
  #scale_colour_manual(values = wes_palette("Darjeeling1")) +
  scale_colour_manual(values = cols, limits = c("First", "Second", "Third","All")) +
  ylim(0, 0.3) +
  guides(col = guide_legend("Measurement")) +
  theme(axis.text.y = element_blank(), axis.ticks.y = element_blank(), legend.position = c(0.90, 0.2), plot.title = element_text(hjust = 0.5)) +
  coord_flip()

forest_rpt_outputs

# Save an object as a file, ready to import into other rmd document
saveRDS(rpt_outputs, file = "rpt_outputs.rds")
```
```{r}
##forest plot showing r estimate and 95% CI, conditions grouped according to CS+
cols <- c("Across" = "#708090","Green_Blue" = "#009E73", "Blue_Green" = "#56B4E9", "All" = "#008B8B", "Third" = "#20B2AA", "Second" = "#00CED1", "First" = "#AFEEEE")

test_figure <- ggplot(data = rpt_outputs, aes(x = conditions, y = R, colour = conditions)) +
  geom_errorbar(aes(ymin = lowCI, ymax = highCI), width = 0.3, position = position_dodge(0.3), size = 1.1) +
  geom_point(aes(x = conditions, y = R), position = position_dodge(0.3), size = 2.9) +
  geom_hline(yintercept = 0, lty = "dotted") +
  labs(x = "Condition", y = "Repeatability (R)", title = "Repeatabiltiy of Aversive Learning in Different Conditions") +
  facet_col(vars(CS), scales = "free_y", space = "free") + #facet_col produces a better forest plot than facet_wrap
  #scale_colour_manual(values = wes_palette("Darjeeling1")) +
  scale_colour_manual(values = cols, limits = c("First", "Second", "Third","All")) +
  ylim(0, 0.3) +
  guides(col = guide_legend("Measurement")) +
  theme(axis.text.y = element_blank(), axis.ticks.y = element_blank(), legend.position = c(0.90, 0.2), plot.title = element_text(hjust = 0.5)) +
  coord_flip()

test_figure

```


```{r}
group(a = "REDCS", b = "REDNON", c = 1, d = e1_new) -> group_1_new #DF of red and yellow

group(a = "GRECS", b = "GRENON", c = 2, d = e1_new) -> group_2_new #DF of green and blue

group(a = "CHKCS", b = "CHKNON", c = 3, d = e1_new) -> group_3_new #DF of check and grey

group(a = "ORACS", b = "ORANON", c = 4, d = e1_new) -> group_4_new #DF of orange and magenta
```

