---
title: "Import"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

#install.packages("pacman")
pacman::p_load(tidyverse, ggbeeswarm, rptR, lme4, magrittr)

# load functions
source("functions.R") #access to functions in different R script
```

#Import Exp 1
```{r importing experiment 1, warning=FALSE}
## importing csv's & transforming data
path <- paste0("./Data/Experiment 1 Raw Data/Day", 1:16, "/") #creates a section of the raw data filepaths

all_path <- map(path,  ~list.files(path = .)[str_detect(list.files(path = .), ".csv")] ) %>% map2(.,path,~ paste0(.y, .x)) #creates a list of the complete raw data filepaths

e1_data <- map(unlist(all_path), import_csv) %>% #uses import_csv function from the source script functions.R to modify the raw data into R suitable structure
  bind_rows() %>% as_tibble() %>% #makes the data frame a tibble
  group_by(filepath, date, marking, type, test, unit, variable, arena) %>% #groups columns for summarising
  summarise(total = sum(number)) %>% #summarises time spent
  filter(variable == "ZONE_TIMERS") %>% #filters the necessary measurement "ZONE TIMERS"
  group_by(type, marking, test, unit, filepath, date) %>%
  summarise(sum_time = sum(total), arena = unique(arena)) %>% 
  arrange(filepath, marking, type, test) %>% #arranges variables in desirable order
  mutate(time_min = if_else(type == "BASELINE", sum_time/5, sum_time/1)) %>% #standardises BASELINE and PROBE to per minute
  add_day %>% add_exp %>% add_zone %>% add_tod %>% add_learning %>% add_expgroup %>% #adding variables
  mutate(day = as.numeric(day)) #changes day variable to numeric 
```

##Import Missing Data 
```{r importing missing data experiment 1, warning = F}
path <- paste0("./Data/Experiment 1 Raw Data/Day9_Missing_Data/")

all_path <- map(path,  ~list.files(path = .)[str_detect(list.files(path = .), ".csv")] ) %>% map2(.,path,~ paste0(.y, .x))

missing_data <- map(unlist(all_path), import_csv) %>% bind_rows() %>% as_tibble() %>% group_by(filepath, date, marking, type, test, unit, variable, arena) %>% summarise(total = sum(number), mean = mean(number)) %>% filter(variable == "ZONE_TIMERS") %>% group_by(type, marking, test, unit, filepath, date) %>% summarise(sum_time = sum(total), arena = unique(arena)) %>% arrange(filepath, marking, type, test) %>% mutate(time_min = if_else(type == "BASELINE", sum_time/5, sum_time/1)) %>% 
                    mutate(day = case_when (grepl("2019-07-09", date) ~ "9")) %>% 
                    mutate(exp = case_when (grepl("MOBASELINE", filepath) ~ "MAGORA"))  %>% 
                    mutate(zone = case_when (grepl("CS", test) ~ "CS",
                                             grepl("NON", test) ~ "NON")) %>%
                    mutate(tod = case_when (grepl("PM", filepath) ~ "PM")) %>%
                    mutate(learning = case_when (grepl("2019-07-09", date) ~ "reverse")) %>%
                    mutate(exp_group = case_when (grepl("MAGORA", exp) ~ "4")) %>%
                    mutate(day = as.numeric(day))

missing_probe <- read.csv("./Data/Missing Data/missing_probe.csv") #loads missing probe data csv into a df

missing_probe %<>% mutate(date = as.Date(date)) %>% mutate(marking = as.character(marking)) %>%
                   mutate(test = as.character(test)) %>% mutate (filepath = as.character(filepath)) %>%
                   mutate(arena = as.character(arena)) %>% mutate(day = as.numeric(day)) %>%
                   mutate(exp = as.character(exp)) %>% mutate(zone = as.character(zone)) %>%
                   mutate(tod = as.character(tod)) %>% mutate(learning = as.character(learning)) %>%
                   mutate(exp_group = as.character(exp_group))

full_join(missing_data, missing_probe) -> new_missing #joins the missing baseline and probe dfs
```

##Filtering appropriate time periods 
```{r, Reduce data to what we want to analyse}
##filters dfs for wanted BASELINE and PROBE times and creates difference (response variable)
new_missing %>% 
  filter(unit %in% c("UNIT1", "UNIT2", "UNIT3", "UNIT4", "UNIT5", "UNIT6", "PROBE1", "PROBE2")) %>% #gets data for all 30 minutes of BASELINE and first two minutes of PROBE
  group_by(type, marking, test, day) %>%
  summarise(time = mean(time_min), arena = unique(arena)) %>% add_diff -> missing_filter 

missing_filter %<>% mutate(filepath = fp) #gets time spent in BASELINE - PROBE

e1_data %>% filter(unit %in% c("UNIT1", "UNIT2", "UNIT3", "UNIT4", "UNIT5", "UNIT6", "PROBE1", "PROBE2")) %>%
  group_by(type, marking, test, filepath, day) %>%
  summarise(time = mean(time_min), arena = unique(arena)) %>%
  add_diff -> e1_filter

new_missing %>% filter(unit %in% c("UNIT5", "UNIT6", "PROBE1", "PROBE2")) %>% #gets data for last 10 minutes of BASELINE and first two minutes of PROBE
  group_by(type, marking, test, day) %>%
  summarise(time = mean(time_min), arena = unique(arena)) %>%
  add_diff -> missing_filter_reduced

missing_filter_reduced %<>% mutate(filepath = fp)

e1_data %>% filter(unit %in% c("UNIT5", "UNIT6", "PROBE1", "PROBE2")) %>%
  group_by(type, marking, test, filepath, day) %>%
  summarise(time = mean(time_min), arena = unique(arena)) %>%
  add_diff -> e1_filter_reduced
```

##Import Size Data Exp 1
```{r Importing data for size variable}
##adding in size data
#fishIDs are not on the size csv, only markings - have to first match markings with fishIDs
merge <- read.csv("./Data/Experiment 1 Size and ID Data/e1_tank_marking_fishID.csv") #putting experiment 1 fishID and marking data into a df
size <- read.csv("./Data/Experiment 1 Size and ID Data/e1_size.csv") #putting experiment 1 size and marking data into a df

merge %<>% mutate(tankmark = paste0(tank, mark)) #creating variable with tank and marking to match later in a join
size %<>% mutate(tankmark = paste0(tank, mark)) 

full_join(e1_filter, missing_filter) -> data_e1 #merging missing and experiment 1 data into one df
full_join(e1_filter_reduced, missing_filter_reduced) -> data_e1_reduced_time #the same but for reduced baseline time

data_e1 %<>% mutate(fishID = marking) #changes name of "marking" variable to "fishID"
data_e1_reduced_time %<>% mutate(fishID = marking)

left_join(merge, size, by = "tankmark") -> jointed #merges fishID/marking and size/marking dfs
left_join(jointed, data_e1, by = "fishID") -> dat_merge #adds size data to df
left_join(jointed, data_e1_reduced_time, by = "fishID") -> dat_merge_reduced

dat_merge %>% mutate(fish_size = pi*((fish_length/2)*(fish_width/2))) -> exp1 #gets the ellipse area for the fish size
dat_merge_reduced %>% mutate(fish_size = pi*((fish_length/2)*(fish_width/2))) -> exp1_reduced

exp1 %<>% add_zone %>% add_exp %>% add_expgroup %>% add_learning3 %>% add_set #adds necessary variables
exp1_reduced %<>% add_zone %>% add_exp %>% add_expgroup %>% add_learning3 %>% add_set
```

#Import Exp 2
```{r importing experiment 2, warning = F}
##importing raw data forexperiment 2
path <- paste0("./data/Experiment 2 Raw Data/Day", 1:8, "/")

all_path <- map(path,  ~list.files(path = .)[str_detect(list.files(path = .), ".csv")] ) %>% map2(.,path,~ paste0(.y, .x))

e2_data <- map(unlist(all_path), import_csv) %>% bind_rows() %>% as_tibble() %>% group_by(filepath, date, marking, type, test, unit, variable, arena) %>% summarise(total = sum(number)) %>% filter(variable == "ZONE_TIMERS") %>% group_by(type, marking, test, unit, filepath, date) %>% summarise(sum_time = sum(total), arena = unique(arena)) %>% arrange(filepath, marking, type, test) %>% mutate(time_min = if_else(type == "BASELINE", sum_time/5, sum_time/1)) %>% add_day2 %>% add_exp %>% add_zone %>% add_tod %>% add_learning2 %>% add_expgroup %>% mutate(day = as.numeric(day))
```

##Import Siza Data Exp 2
```{r size data exp 2, warning = F}
##importing size data for experiment 2
jointed2 <- read.csv("./Data/Experiment 2 Size and ID Data/e2_fishID_size.csv")

e2_data %>% filter(unit %in% c("UNIT1", "UNIT2", "UNIT3", "UNIT4", "UNIT5", "UNIT6", "PROBE1", "PROBE2")) %>%
  group_by(type, marking, test, filepath, day) %>%
  summarise(time = mean(time_min), arena = unique(arena)) %>%
               add_diff -> e2_filter

e2_data %>% filter(unit %in% c("UNIT5", "UNIT6", "PROBE1", "PROBE2")) %>%
  group_by(type, marking, test, filepath, day) %>%
  summarise(time = mean(time_min), arena = unique(arena)) %>%
               add_diff -> e2_filter_reduced

e2_filter %<>% mutate(fishID = marking) #corrects variable name from marking to fishID 
e2_filter_reduced %<>% mutate(fishID = marking)

left_join(jointed2, e2_filter, by = "fishID") -> dat_merge2 
left_join(jointed2, e2_filter_reduced, by = "fishID") -> dat_merge2_reduced

dat_merge2 %>% mutate(fish_size = pi*((fish_length/2)*(fish_width/2))) -> exp2_size
dat_merge2_reduced %>% mutate(fish_size = pi*((fish_length/2)*(fish_width/2))) -> exp2_size_reduced

#function that adds imoprtant variables back to the dataframe
add_variables <- function(x) {
  x %>% add_zone %>% add_exp %>% add_expgroup %>% add_learning2 %>% add_set2 
}

add_variables(exp2_size) -> exp2
add_variables(exp2_size_reduced) -> exp2_reduced 
```

##Tidying Both Exps
```{r selecting & renaming, warning = F}
##selecting which columns to keep and renaming so both experimental data frames have the same variables
select_rename <- function(x) {
  x %>% select(tank.x, mark.x, updatedsex, fishID, fish_length, fish_width, test, filepath, day, BASELINE, PROBE, difference, fish_size, zone, exp, exp_group, learning, set) %>% rename(tank = tank.x, mark = mark.x, sex = updatedsex) -> x
}

select_rename(exp1) -> e1_selected

e1_selected <- e1_selected[-1529,] #removes additional observation of NAs that select rename function creates

select_rename(exp1_reduced) -> e1_selected_reduced

exp2 %>% select(-marking) -> e2_selected #removes unnecessary variable

exp2_reduced %>% select(-marking) -> e2_selected_reduced

## removing non-CS value as its only a mirror of CS
cs_only(e1_selected) -> e1
cs_only(e2_selected) -> e2
cs_only(e1_selected_reduced) -> e1_reduced
cs_only(e2_selected_reduced) -> e2_reduced

full_join(e1, e2) -> bothexp

e1 %<>% add_tod() #adding time of day to DF

#changing all character variables to factors in the DFs
e1[sapply(e1, is.character)] <- lapply(e1[sapply(e1, is.character)], as.factor)

e2[sapply(e2, is.character)] <- lapply(e2[sapply(e2, is.character)], as.factor)
```

#Filtering Single Conditions
##Filtering GB Condition
```{r filtering and joining GREBLU, warning = F}
## GREBLU filter function
gb_only <- function (x) {
  x %>% filter(exp == "GREBLU")
}
#filtering only GREBLU assay
gb_only(e1) -> e1gb
gb_only(e2) -> e2gb
gb_only(e1_reduced) -> e1gb_reduced
gb_only(e2_reduced) -> e2gb_reduced

#joining GREBLU assays in experiment 1 and 2
full_join(e1gb, e2gb) -> allgb

full_join(e1gb_reduced, e2gb_reduced) -> allgb_reduced
```

##Filtering BG Condition
```{r filtering and joining BLUGRE, warning = F}
#filtering only BLUGRE assay
e1 %>% filter(exp == "BLUGRE") -> e1bg

e2 %>% filter(exp == "BLUGRE") -> e2bg

e1_reduced %>% filter(exp == "BLUGRE") -> e1bg_reduced

e2_reduced %>% filter(exp == "BLUGRE") -> e2bg_reduced

full_join(e1bg, e2bg) -> allbg

full_join(e1bg_reduced, e2bg_reduced) -> allbg_reduced
```

##Joining Conditions & Experiments
```{r Creating data sets of combined conditions and experiments, warning = F}
##joining single conditions and whole experiments
#joining GREBLU and BLUGRE assays
full_join(allgb, allbg) -> allgbbg

full_join(allgb_reduced, allbg_reduced) -> allgbbg_reduced

#joining both full experiments
full_join(e1, e2) -> allexp

full_join(e1_reduced, e2_reduced) -> allexp_reduced
```

#Creating Measurement Sets
```{r making measurement sets for single conditions}
## filtering single conditions GREBLU and BLUGRE in groups when they were measured
allgbbg %>% filter(set %in% c("firstg","firstb")) -> first

allgbbg %>% filter(set %in% c("secondg","secondb")) -> second

allgbbg %>% filter(set %in% c("thirdg","thirdb")) -> third

allgbbg_reduced %>% filter(set %in% c("firstg","firstb")) -> first_reduced

allgbbg_reduced %>% filter(set %in% c("secondg","secondb")) -> second_reduced

allgbbg_reduced %>% filter(set %in% c("thirdg","thirdb")) -> third_reduced

#filtering single conditions
allgb %>% filter(set %in% c("firstg","secondg")) -> first_second_g

allbg %>% filter(set %in% c("firstb","secondb")) -> first_second_b

allgb %>% filter(set %in% c("firstg","thirdg")) -> first_third_g

allbg %>% filter(set %in% c("firstb","thirdb")) -> first_third_b

allgb %>% filter(set %in% c("secondg","thirdg")) -> second_third_g

allbg %>% filter(set %in% c("secondb","thirdb")) -> second_third_b

allgb_reduced %>% filter(set %in% c("firstg","secondg")) -> first_second_g_reduced

allbg_reduced %>% filter(set %in% c("firstb","secondb")) -> first_second_b_reduced

allgb_reduced %>% filter(set %in% c("firstg","thirdg")) -> first_third_g_reduced

allbg_reduced %>% filter(set %in% c("firstb","thirdb")) -> first_third_b_reduced

allgb_reduced %>% filter(set %in% c("secondg","thirdg")) -> second_third_g_reduced

allbg_reduced %>% filter(set %in% c("secondb","thirdb")) -> second_third_b_reduced
```

#Removing Size Data
```{r selecting out size data in data sets}
## selecting out size data for models to analyse effect of keeping size in models vs not
#function for removing size data
rm_size <- function(a) {
  arrange(a, fishID) -> x
  x %>% select(-fish_length, -fish_width, -fish_size)
}

rm_size(allgb)  -> allgb_no_size
rm_size(e2gb)   -> e2gb_no_size
rm_size(e2bg)   -> e2bg_no_size
rm_size(e1)     -> e1_no_size
rm_size(allbg)  -> allbg_no_size
rm_size(first)  -> first_no_size
rm_size(second) -> second_no_size
rm_size(third)  -> third_no_size
```

#Making Col Preference DFs
```{r filtering and grouping colours exp1}
e1_selected %>% add_tod() -> e1_new #original DF before  it was filtered for only the CS

e2_selected %>% add_tod() -> e2_new

##group RED/YEL GRE/BLU CHK/GRY ORA/MAG to assess colour preference in the baseline period
group <- function(a = "", b = "", c = "", d = "") {
  d %>% filter(exp_group == c) %>% filter(test %in% c(a, b)) -> x
}

group(a = "REDCS", b = "REDNON", c = 1, d = e1_new) -> group_1 #DF of red and yellow

group(a = "GRECS", b = "GRENON", c = 2, d = e1_new) -> group_2 #DF of green and blue

group(a = "GRYCS", b = "GRYNON", c = 3, d = e1_new) -> group_3 #DF of grey and check

group(a = "ORACS", b = "ORANON", c = 4, d = e1_new) -> group_4 #DF of orange and magenta

##experiment 2
group(a = "GRECS", b = "GRENON", c = 2, d = e2_new) -> group_exp2
```

#Separating Sex
##Separating Sex in Rpt DFs
```{r separate into two dfs - male & female}
##filtering male and female data sets

#function for filtering sex
filter_sex <- function(df, x = "", y = "") {
  df %>% filter(sex == "male") -> filtered_male 
  assign(x, filtered_male, envir = .GlobalEnv)
  df %>% filter(sex == "female") -> filtered_female
  assign(y, filtered_female,envir = .GlobalEnv)
}

filter_sex(e1, x = "e1_male", y = "e1_female")
filter_sex(e2, x = "e2_male", y = "e2_female")
filter_sex(allgb, x = "allgb_male", y = "allgb_female")
filter_sex(allbg, x = "allbg_male", y = "allbg_female")
filter_sex(first, x = "first_male", y = "first_female")
filter_sex(second, x = "second_male", y = "second_female")
filter_sex(third, x = "third_male", y = "third_female")
filter_sex(allgbbg, x = "allgbbg_male", y = "allgbbg_female")
```

##Separating Sex in Pref DFs
```{r filtering sex for preference data}
#filtering preference data
filter_sex <- function(df, x = "", y = "") {
  df %>% filter(sex == "male") -> filtered_male 
  assign(x, filtered_male, envir = .GlobalEnv)
  df %>% filter(sex == "female") -> filtered_female
  assign(y, filtered_female,envir = .GlobalEnv)
}

filter_sex(group_1, x = "group_1_male", y = "group_1_female")
filter_sex(group_2, x = "group_2_male", y = "group_2_female")
filter_sex(group_3, x = "group_3_male", y = "group_3_female")
filter_sex(group_4, x = "group_4_male", y = "group_4_female")
```

#Rmd Output Prep
```{r}
# Save an object as a file, ready to import into other rmd document
save(e1_data, e1, e2, e1_male, e1_female, 
     allgb, allbg, 
     allgb_male, allgb_female, allbg_male, allbg_female,
     allgbbg,
     allgbbg_male, allgbbg_female,
     first, second, third, 
     first_male, first_female, 
     second_male, second_female,
     third_male, third_female,
     group_1, group_2, group_3, group_4,
     group_1_male, group_1_female, 
     group_2_male, group_2_female,
     group_3_male, group_3_female,
     group_4_male, group_4_female,
     file = "./Data/processed_data.Rdata")
```

# Import Pilot Data   
##Import Pilot Day 1 & 2
```{r}
#Days 1 & 2 had 2 minute probe phases
path <- paste0("./Data/volttest/day", 1:2, "/") #creates a section of the raw data filepaths

all_path <- map(path,  ~list.files(path = .)[str_detect(list.files(path = .), ".csv")] ) %>% map2(.,path,~ paste0(.y, .x)) 

volt_2 <- map(unlist(all_path), import_csv) %>% #uses import_csv function from the source script functions.R to modify the raw data into R suitable structure
  bind_rows() %>% as_tibble() %>% #makes the data frame a tibble
  group_by(filepath, date, marking, type, test, unit, variable, arena) %>% #groups columns for summarising
  summarise(total = sum(number)) %>% #summarises time spent
  filter(variable == "ZONE_TIMERS") %>% #filters the necessary measurement "ZONE TIMERS"
  group_by(type, marking, test, unit, filepath, date) %>%
  summarise(sum_time = sum(total), arena = unique(arena)) %>% 
  arrange(filepath, marking, type, test) %>% #arranges variables in desireable order
  mutate(time_min = if_else(type == "BASELINE", sum_time/5, sum_time/1)) %>% #standardises BASELINE and PROBE to per minute
  add_day

head(volt_2)
```

#Import Day 3
```{r}
#Day 3 had a 6 minute probe phases
path <- paste0("./Data/volttest/day", 3, "/") #creates a section of the raw data filepaths

all_path <- map(path,  ~list.files(path = .)[str_detect(list.files(path = .), ".csv")] ) %>% map2(.,path,~ paste0(.y, .x)) 

volt_5 <- map(unlist(all_path), import_csv) %>% #uses import_csv function from the source script functions.R to modify the raw data into R suitable structure
  bind_rows() %>% as_tibble() %>% #makes the data frame a tibble
  group_by(filepath, date, marking, type, test, unit, variable, arena) %>% #groups columns for summarising
  summarise(total = sum(number)) %>% #summarises time spent
  filter(variable == "ZONE_TIMERS") %>% #filters the necessary measurement "ZONE TIMERS"
  group_by(type, marking, test, unit, filepath, date) %>%
  summarise(sum_time = sum(total), arena = unique(arena)) %>% 
  arrange(filepath, marking, type, test) %>% #arranges variables in desirable order
  mutate(time_min = if_else(type == "BASELINE", sum_time/5, sum_time/3)) %>% #standardises BASELINE and PROBE to per minute
  add_day

head(volt_5)
```

#Joining Data Sets
```{r}
#can now join after importing separately due to different probe times
volt_2 %>%
  group_by(marking, filepath, day, type, test) %>%
  summarise(time = mean(time_min), arena = unique(arena)) %>%
  add_diff -> dat_2

volt_5 %>%
    group_by(marking, filepath, day, type, test) %>% 
  summarise(time = mean(time_min), arena = unique(arena)) %>%
  add_diff -> dat_5

full_join(dat_2, dat_5) %>%  mutate(voltage = case_when(grepl("BG5", filepath) ~ "5",
                             grepl("BG7", filepath) ~ "7",
                             grepl("BG9", filepath) ~ "9")) -> volt_data
```

## Saving pilot data
```{r}
save(volt_data, file = "./Data/pilot_data.Rdata")
```