---
title: "Analysis"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

#install.packages("pacman")
pacman::p_load(tidyverse, ggbeeswarm, rptR, lme4, magrittr, sjPlot, glmmTMB, lmerTest)

# loading processed data
load("./Data/processed_data.Rdata")
```

#Learning models 
##Learning Exp1
```{r}
##basic model
learn_model_e1 <- lmer(difference ~ scale(day) + sex + scale(fish_size) + learning + (1 | exp) + (1 | fishID), data = e1) #z-scaling, if you scale fish size you have to scale day as well

summary(learn_model_e1) #experiment 1 93 levels

learn_model_e1_male <- lmer(difference ~ scale(day) + scale(fish_size) + learning + (1 | exp) + (1 | fishID), data = e1_male)

learn_model_e1_male 

learn_model_e1_female <- lmer(difference ~ scale(day) + scale(fish_size) + learning + (1 | exp) + (1 | fishID), data = e1_female)

learn_model_e1_female 
```

##Learning Exp2
```{r}
learn_model_e2 <- lmer(difference ~ scale(day) + sex + scale(fish_size) + learning + (1 | exp) + (1 | fishID), data = e2)

summary(learn_model_e2)

learn_model_e2_male <- lmer(difference ~ scale(day) + scale(fish_size) + learning + (1 | exp) + (1 | fishID), data = e2_male)

learn_model_e2_male 

learn_model_e2_female <- lmer(difference ~ scale(day) + scale(fish_size) + learning + (1 | exp) + (1 | fishID), data = e2_female)

learn_model_e2_female 

str(e2)

str(e1)
```

#Repeatability Models   
##Across Conditions Repeatabilties
```{r Exp 1 Analysis}
#repeatability outputs for across 8 conditions
  
#repetability model function for mixed sexes
rpt_sex <- function(x, y = "") {
  
x <- rpt(difference ~ sex + (1 | fishID), grname = "fishID", data = x, datatype = "Gaussian", nboot = 1000, npermut = 1000, adjusted = FALSE) #estimate of enhanced agree repeatability, differing from adjusted since the fixed effects variance is included in the denominator

assign(y, x, envir = .GlobalEnv) #assigns output to global environment from within function

x
}

rpt_nosex <- function(x, y = "") {
  
x <- rpt(difference ~ 1 + (1 | fishID), grname = "fishID", data = x, datatype = "Gaussian", nboot = 1000, npermut = 1000, adjusted = FALSE)

assign(y, x, envir = .GlobalEnv) #assigns output to global environment from within function

x
}
```

###R Across Con
```{r}
rpt_sex(e1, y = "rpt_e1") #across conditions rpt model
rpt_nosex(e1_male, y = "rpt_e1_male") #males only
rpt_nosex(e1_female, y = "rpt_e1_female") #females only
```

##Single Condition Repeatabilties
```{r repeatabilities in single condition}
#Green/Blue sexes separated 
rpt_nosex(allgb_male, y = "rpt_allgb_male")
rpt_nosex(allgb_female, y = "rpt_allgb_female")

#Blue/Green sexes separated
rpt_nosex(allbg_male, y = "rpt_allbg_male")
rpt_nosex(allbg_female, y = "rpt_allbg_female")
```

###R Green/Blue
```{r}
rpt_sex(allgb, y = "rpt_allgb") #all GREBLU
```

###R Blue/Green
```{r}
rpt_sex(allbg, y = "rpt_allbg") #all BLUGRE
```

##Rpt Measurement Sets 
```{r Repeatabilties of Single Conditions Measurement Sets}
#analysis of grouped measurements, first, second, third, all
rpt_set_sex <- function(x, y = "") {
  
x <- rpt(difference ~ set + sex + (1 | fishID), grname = "fishID", data = x, datatype = "Gaussian", nboot = 1000, npermut = 1000)

assign(y, x, envir = .GlobalEnv) #assigns output to global environment from within function

x
}

##rpt of Green/Blue & Blue/Green first measurement set
rpt_set_sex(first, y = "rpt_first")

##rpt of Green/Blue & Blue/Green second measurement set
rpt_set_sex(second, y = "rpt_second")

##rpt of Green/Blue & Blue/Green second measurement set
rpt_set_sex(third, y = "rpt_third")

##rpt of Green/Blue & Blue/Green all three measurement sets
rpt_set_sex(allgbbg, y = "rpt_allgbbg")


rpt_set <- function(x, y = "") {
  
x <- rpt(difference ~ set + (1 | fishID), grname = "fishID", data = x, datatype = "Gaussian", nboot = 10000, npermut = 10000)

assign(y, x, envir = .GlobalEnv) #assigns output to global environment from within function

x
}

##rpt of Green/Blue & Blue/Green first measurement set
rpt_set(first_male, y = "rpt_first_male") #males only
rpt_set(first_female, y = "rpt_first_female") #females only

##rpt of Green/Blue & Blue/Green second measurement set
rpt_set(second_male, y = "rpt_second_male")
rpt_set(second_female, y = "rpt_second_female")

##rpt of Green/Blue & Blue/Green second measurement set
rpt_set(third_male, y = "rpt_third_male")
rpt_set(third_female, y = "rpt_third_female")

##rpt of Green/Blue & Blue/Green all three measurement sets
rpt_set(allgbbg_male, y = "rpt_allgbbg_male")
rpt_set(allgbbg_female, y = "rpt_allgbbg_female")
```

##Repeatability of Colour Preference
```{r repeatbiltiy of colour preference}
##rpt for colour preference
rpt_pref <- function(x, y = "") { #function that creates df of time spent in one colour over the other in its condition
  
x <- rpt(BASELINE ~ 1 + (1 | fishID), grname = "fishID", data = x, datatype = "Gaussian", nboot = 1000, npermut = 1000)

assign(y, x, envir = .GlobalEnv) #assigns output to global environment from within function

x
}

rpt_pref(group_1, y = "red_pref") #preference for red colour
rpt_pref(group_2, y = "green_pref") #preference for green colour
rpt_pref(group_3, y = "grey_pref") #preference for check colour
rpt_pref(group_4, y = "orange_pref") #preference for orange colour

rpt_pref(group_1_male, y = "red_pref_male")
rpt_pref(group_1_female, y = "red_pref_female")

rpt_pref(group_2_male, y = "green_pref_male")
rpt_pref(group_2_female, y = "green_pref_female")

rpt_pref(group_3_male, y = "check_pref_male")
rpt_pref(group_3_female, y = "check_pref_female")

rpt_pref(group_4_male, y = "orange_pref_male")
rpt_pref(group_4_female, y = "orange_pref_female")
```


#Organising Outputs
```{r Formatting Repeatabiltiy Outputs} 
#changes number of digits in output to 3
options(digits = 3)

##function for getting vector of results for rpt analysis
rpt_output <- function(w){
  data.frame(c(w$R,  
               w$se,
               w$CI_emp,
               w$P)) -> y
return(y)
}

##outcomes as data frames
rpt_output(rpt_e1) -> Across_Conditions

rpt_output(rpt_allgb) -> Green_Blue
rpt_output(rpt_allbg) -> Blue_Green

rpt_output(rpt_first) -> First
rpt_output(rpt_second) -> Second
rpt_output(rpt_third) -> Third

rpt_output(rpt_allgbbg) -> All

rpt_output(red_pref) -> Red
rpt_output(green_pref) -> Green
rpt_output(grey_pref) -> Grey
rpt_output(orange_pref) -> Orange
```

##Renaming Rpt Outputs
```{r}
#function for renaming output variables
rename_output_func <- function(x) {
  
   x %>% rename(R = fishID, lowCI = X2.5., highCI = X97.5.)
}

#function that changes first column named rownames to conditions
rownames_col_to_con <- function(x) {

x <- cbind(conditions = rownames(x), x)

x
}

#funtion that binds outputs together
rename_rm_col <- function(y, z) {

rbind(y) -> x1

rownames(x1) <- z

x1 %>% rownames_col_to_con -> x2

rename_output_func(x2) -> x
}

rename_rm_col(rbind(Across_Conditions, Green_Blue, Blue_Green, First, Second, Third, All), c("Across", "Green_Blue", "Blue_Green", "First", "Second", "Third", "All")) -> rpt_outputs

rename_rm_col(rbind(Red, Green, Grey, Orange), c("Red", "Green", "Grey", "Orange")) -> pref_outputs
```

#Colour Preference
##Colour Preference Exp1 Data Wrangling
```{r Colour Preference}
red <- "Red"
gre <- "Green"
gry <- "Grey"
ora <- "Orange"

#making four groups, each share the same colours
group_1 %>% mutate(pref = BASELINE, stim = red) -> df_red_pref  
group_2 %>% mutate(pref = BASELINE, stim = gre) -> df_gre_pref
group_3 %>% mutate(pref = BASELINE, stim = gry) -> df_gry_pref
group_4 %>% mutate(pref = BASELINE, stim = ora) -> df_ora_pref

full_join(df_red_pref, df_gre_pref) -> red_gre #first step to join all col pref DF's

full_join(red_gre, df_gry_pref) -> red_gre_gry #second step

full_join(red_gre_gry, df_ora_pref) -> col_pref #all col prefs together in  DF

col_pref <- mutate_if(col_pref, is.character, as.factor) #changed chr to fctr
```

##Rpt Outputs Sex
```{r rpt outputs in sexes}
## separated sexes
rpt_output(rpt_e1_male) -> Across_Male
rpt_output(rpt_e1_female) -> Across_Female

# all green male and female
rpt_output(rpt_allgb_male) -> GreenBlue_Male
rpt_output(rpt_allgb_female) -> GreenBlue_Female

# all bluemale and female
rpt_output(rpt_allbg_male) -> BlueGreen_Male
rpt_output(rpt_allbg_female) -> BlueGreen_Female

#grouped measurements blue and green
rpt_output(rpt_first_male) -> First_Male
rpt_output(rpt_first_female) -> First_Female

rpt_output(rpt_second_male) -> Second_Male
rpt_output(rpt_second_female) -> Second_Female

rpt_output(rpt_third_male) -> Third_Male
rpt_output(rpt_third_female) -> Third_Female

rpt_output(rpt_allgbbg_male) -> All_Male
rpt_output(rpt_allgbbg_female) -> All_Female

#colour preference male and female
rpt_output(red_pref_male) -> red_pref_male_output
rpt_output(red_pref_female) -> red_pref_female_output

rpt_output(green_pref_male) -> green_pref_male_output
rpt_output(green_pref_female) -> green_pref_female_output

rpt_output(check_pref_male) -> check_pref_male_output
rpt_output(check_pref_female) -> check_pref_female_output

rpt_output(orange_pref_male) -> orange_pref_male_output
rpt_output(orange_pref_female) -> orange_pref_female_output

rename_rm_col(rbind(Across_Male, Across_Female, GreenBlue_Male, GreenBlue_Female, BlueGreen_Male, BlueGreen_Female, First_Male, First_Female, Second_Male, Second_Female, Third_Male, Third_Female, All_Male, All_Female), c("Across_Male", "Across_Female", "Green/Blue_Male", "Green/Blue_Female", "Blue/Green_Male", "Blue/Green_Female", "First_Male", "First_Female", "Second_Male", "Second_Female", "Third_Male", "Third_Female", "All_Male", "All_Female")) -> rpt_outputs_sex #df rpt outputs sex separated

rename_rm_col(rbind(red_pref_male_output, red_pref_female_output, green_pref_male_output, green_pref_female_output, check_pref_male_output, check_pref_female_output, orange_pref_male_output, orange_pref_female_output), c("red_pref_male_output", "red_pref_female_output", "green_pref_male_output", "green_pref_female_output", "grey_pref_male_output", "grey_pref_female_output", "orange_pref_male_output", "orange_pref_female_output")) -> pref_outputs_sex #df pref rpt outputs sex separated


full_join(rpt_outputs, rpt_outputs_sex) -> rpt_outputs_all #repeatability output with original and also sexes split
full_join(pref_outputs, pref_outputs_sex) -> pref_outputs_all
```

# Saving Outputs
```{r}
save.image("02_Run Models_Workspace.RData")
```

#Contrast Analysis
```{r}
rpt_e1_male #1

rpt_e1_female #2

#Analysis to find differences
##Step 1: Unlist distributions from rptr models and examine histograms 
rptr_male_boot <- unlist(rpt_e1_male$R_boot)
hist(rptr_male_boot, breaks = 50)
rptr_female_boot <- unlist(rpt_e1_female$R_boot)
hist(rptr_female_boot, breaks = 50)

#Step 2: Find the difference between bootstrap distributions and examine histogram

rptr_diff <- rptr_male_boot - rptr_female_boot
hist(rptr_diff, breaks = 50)

#Step 3: Find mean of the new distribution (difference between rptr models)

m3 <- mean(rptr_diff)
m3

#Step 4: Find quantiles at 0.025 and 0.975 (these two become your lower bound and upper bound 95% CI)

q <- quantile(rptr_diff, c(0.025, 0.975))
q

### males are higher, but not significantly different from females (because the 95% CI overlaps zero)

# work out how to plot!

###NEED TO CREATE A DF WITH CONTRASTS ANALYSES AND MERGE WITH RPT OUTPUTS ALL TO MAKE NEW SUPP PLOT###
###COULD TAKE OUT VARIABLES ALREADY SHOWN IN RESULTS###
```

##Plot Contrast Analysis
```{r}
df_contrast_learn <- tibble(
  Condition = c("Male", "Female", "Contrast"),
  r = c(e1_male$R$fishID,e1_female$R$fishID, m3),
  ci.lb = c(e1_male$CI_emp$`2.5%`,e1_female$CI_emp$`2.5%`,-0.01),
  ci.ub = c(e1_male$CI_emp$`97.5%`,e1_female$CI_emp$`97.5%`, 0.38),
Endpoint = c("Total distance", "Total distance", "Total distance"))

df_contrast_learn
```
```{r}
plot_Tot_Dist_rptr <- ggplot(Tot_Dist_rptr, aes(x=Condition, y=r, colour=Condition)) +
  geom_errorbar(aes(ymin=ci.lb, ymax=ci.ub), width = 0, position = position_dodge(0.3), size=1.1) +
  geom_point(aes(x = Condition, y = r), position = position_dodge(0.3),size=3)+
  scale_color_manual(values=c("#000000", "#339900", "#FF9900"))+
  geom_hline(yintercept = 0, lty = "dotted") +
  labs(y = "r") +
  labs(title = "Repeatability estimates", subtitle = "Total distance")+
  coord_flip()+
   theme(axis.title.y=element_blank(),
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank())+
  ylim(-0.2, 0.8) +
  theme(axis.title.x = element_blank(),
        axis.text.x = element_blank())+
  theme(legend.position="top")
plot_Tot_Dist_rptr
```

#Repeatability Tables
```{r}
# write.table(rpt_outputs, file = "rpt_outputs_table.csv", sep = ",", row.names = FALSE) #exports table to project file
# 
# write.table(rpt_outputs_sex, file = "rpt_outputs_sex_table.csv", sep = ",", row.names = FALSE)
# 
# write.table(rpt_outputs_all, file = "rpt_outputs_all_table.csv", sep = ",", row.names = FALSE)
# 
# write.table(pref_outputs, file = "pref_outputs_table.csv", sep = ",", row.names = FALSE)
# 
# write.table(pref_outputs_sex, file = "pref_outputs_sex_table.csv", sep = ",", row.names = FALSE)
# 
# write.table(pref_outputs_all, file = "pref_outputs_all_table.csv", sep = ",", row.names = FALSE)
```

#Checking Inconsistency in model fishID levels
```{r}
e1 -> test_e1
e1_new -> test_e1_new
group_1 -> test_group_1
group_2 -> test_group_2
group_3 -> test_group_3
group_4 -> test_group_4

fctr_chk <- function(DF) {
DF[sapply(DF, is.character)] <- lapply(DF[sapply(DF, is.character)], 
                                       as.factor)
str(DF)
}

#all models originate from experiment one and should have same amount of fishID levels
#cs_only function is the difference, without it, e1_new has 1 more level
#groups come from e1_new and lose 2 to 3 levels

#some fish don't have fish size data

sum(is.na(e1_new))
sum(is.na(e1))
sum(is.na(e1_new$day))
sum(is.na(e1$day))


fctr_chk(test_e1_new) #100 levels
fctr_chk(test_e1) #99 levels
fctr_chk(test_group_1) #98 levels
fctr_chk(test_group_2) #97 levels
fctr_chk(test_group_3) #97 levels
fctr_chk(test_group_4) #98 levels
```

#Clear Environment
```{r}
#rm(list = ls(all.names = TRUE))
```


