---
title: "Results"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
rm(list=ls())
#install.packages("pacman")
pacman::p_load(tidyverse, readxl, ggbeeswarm, rptR, lme4, ggpubr, ggforce, magrittr, MuMIn)

###included colours are colourblind-friendly###
load("02_Run Models_Workspace.RData")
load("./Data/pilot_data.Rdata")

# model for "Do Zebrafish Show Appropriate Responses in an Aversive Learning Assay?"
learn_mod <- data.frame(coef(summary(learn_model_e1)))
learn_mod$coef_name <- rownames(learn_mod)

# models for "Do Zebrafish Display Colour Preferences and is Preference Repeatable?"    
grey_pref
green_pref
red_pref
orange_pref

# models for "Is Aversive Learning Repeatable Across and Within Conditions?"   
rpt_e1
rpt_allgb
rpt_allbg

# models for "Sex Differences in Repeatability"   
rpt_e1_male
rpt_e1_female
rpt_allbg_male
rpt_allbg_female
```

# Results text 

## Do Zebrafish Show Appropriate Responses in an Aversive Learning Assay?
Zebrafish spent more time avoiding the CS+ following conditioning, showing evidence of learning (`r round(learn_mod$Estimate[learn_mod$coef_name == "(Intercept)"],2)` seconds, SE = `r round(learn_mod$Std..Error[learn_mod$coef_name == "(Intercept)"],3)`, t~`r learn_mod$df[learn_mod$coef_name == "(Intercept)"]`~ = `r round(learn_mod$t.value[learn_mod$coef_name == "(Intercept)"],3)`, P = `r round(learn_mod$Pr...t..[learn_mod$coef_name == "(Intercept)"],3)`). Males avoided the CS+ significantly more than females (`r round(learn_mod$Estimate[learn_mod$coef_name == "sexmale"],3)` seconds, SE = `r round(learn_mod$Std..Error[learn_mod$coef_name == "sexmale"],3)`, t~`r learn_mod$df[learn_mod$coef_name == "sexmale"]`~ = `r round(learn_mod$t.value[learn_mod$coef_name == "sexmale"],3)`, P = `r round(learn_mod$Pr...t..[learn_mod$coef_name == "sexmale"],3)`; Figure 2A), indicating males displayed a stronger learned association response. All other fixed effects did not significantly impact learning (see Supplementary Table 1 for all model outputs).

## Do Zebrafish Display Colour Preferences and is Preference Repeatable?
Zebrafish showed strong relative colour preference in all four conditions (see Figure 2B). In addition, fish exhibited repeatable relative colour preferences which were highly consistent across all four conditions (Figure 3A; Grey: R = `r grey_pref$R`, 95% CI [`r grey_pref$CI_emp[1]` - `r grey_pref$CI_emp[2]`]; Green: R = `r green_pref$R`, 95% CI [`r green_pref$CI_emp[1]` - 
`r green_pref$CI_emp[2]`]; Red: R = `r red_pref$R`, 95% CI [`r red_pref$CI_emp[1]` - `r red_pref$CI_emp[2]`]; Orange: R = `r orange_pref$R`; 95% CI [`r orange_pref$CI_emp[1]` - `r orange_pref$CI_emp[2]`]; see Supplementary Table 2 and 3 for all repeatability estimates).

## Is Aversive Learning Repeatable Across and Within Conditions?
We found very low, albeit statistically significant, repeatability across the eight different conditions (i.e. Experiment 1; R = `r rpt_e1$R`, 95% CI [`r rpt_e1$CI_emp[1]` - `r rpt_e1$CI_emp[2]`], Figure 3B). In Experiment 2, we found low repeatability values within the two different conditions. The repeatability (point-estimate) of the ‘Green/Blue’ condition was even lower than the across-condition estimate (R = `r rpt_allgb$R`, 95% CI [`r rpt_allgb$CI_emp[1]` - `r rpt_allgb$CI_emp[2]`]). In the ‘Blue/Green’ condition, repeatability was higher than the former two estimates; nevertheless, this estimate remained low (R = `r rpt_allbg$R`, 95% CI [`r rpt_allbg$CI_emp[1]` - `r rpt_allbg$CI_emp[2]`]; see also Supplementary Figure 3 for male and female estimates).

# Supplementary Notes   
## Sex Differences in Repeatability   
We found males we more generally more repeatable than females (Figure S3) in aversive learning. We found this result across conditions (males, sample size = `r rpt_e1_male$ngroups`, R = `r rpt_e1_male$R`, 95% CI [`r rpt_e1_male$CI_emp[1]` - `r rpt_e1_male$CI_emp[2]`]; females, sample size = `r rpt_e1_female$ngroups`, R = `r rpt_e1_female$R`, 95% CI [`r rpt_e1_female$CI_emp[1]` - `r rpt_e1_female$CI_emp[2]`]) and in the ‘Blue/Green’ condition (males, sample size = `r rpt_allbg_male$ngroups`, R = `r rpt_allbg_male$R`, 95% CI [`r rpt_allbg_male$CI_emp[1]` - `r rpt_allbg_male$CI_emp[2]`]; females, sample size = `r rpt_allbg_female$ngroups`, R = `r rpt_allbg_female$R`, 95% CI [`r rpt_allbg_female$CI_emp[1]` - `r rpt_allbg_female$CI_emp[2]`])). This result was not anticipated since females are reported to be more repeatable than males in behaviour (Bell et al., 2009).

In relative colour preference, we found males were more repeatable than female in the colours red, grey and orange but not green. Since we are the first to assess the repeatability of colour preference in zebrafish, we cannot compare to the literature, however, the sex differences in colour preference repeatability are mostly consistent with those in the repeatability of aversive learning.

# Supplementary Tables   

## Supplementary Table 1   
```{r}
t1 <- read_excel("Results Tables.xlsx", sheet = 1, skip = 2)
t1[,2:4] <- apply(t1[,2:4], 2, function(x) as.numeric(x))

# estimate and p-values
t1[1:5,c(2,4)] <- round(learn_mod[,c("Estimate","Pr...t..")],3)

# confidence intervals
CIs <- round(data.frame(confint(learn_model_e1)),2)
t1$CI[1:5] <- paste0("'",CIs$X2.5..[4:8], " - ", CIs$X97.5..[4:8])

# variance components
varcor <- data.frame(summary(learn_model_e1)$varcor)
t1$Estimates[7:9] <- round(varcor$vcov[c(3,1,2)],2)
t1$Estimates[t1$Predictors=="ICC"] <- round(varcor$vcov[varcor$grp=="fishID"]/sum(varcor$vcov),2)

# sample sizes   
t1$Estimates[11:12] <- summary(learn_model_e1)$ngrps[c(2,1)]
t1$Estimates[13] <- length(learn_model_e1@resp$y)

# R2
R2 <- as.numeric(round(MuMIn::r.squaredGLMM(learn_model_e1),3))
t1$Estimates[14] <- paste0(R2[1],"/",R2[2])

#write.csv(t1,file="SupplementaryTable1.csv",row.names=F,na="")
```

## Supplementary Table 2    
```{r}
t2 <- read_excel("Results Tables.xlsx", sheet = 2, skip = 1)

# models included in this table
mod_list <- list(rpt_e1,
                 rpt_e1_male,
                 rpt_e1_female,
                 rpt_allgb,
                 rpt_allgb_male,
                 rpt_allgb_female,
                 rpt_allbg,
                 rpt_allbg_male,
                 rpt_allbg_female,
                 rpt_first,
                 rpt_first_male,
                 rpt_first_female,
                 rpt_second,
                 rpt_second_male,
                 rpt_second_female,
                 rpt_third,
                 rpt_third_male,
                 rpt_third_female,
                 rpt_allgbbg,
                 rpt_allgbbg_male,
                 rpt_allgbbg_female)

# position of rows with data in table
pos <- (!is.na(t2$`Repeatability (R)`))

t2$`Repeatability (R)`[pos] <- sapply(mod_list, function(x) round(x$R,3)) %>% unlist 
t2$`95% Confidence Interval`[pos] <- sapply(mod_list, function(x) paste0(round(x$CI_emp[1],3), " - ", round(x$CI_emp[2],3))) %>% unlist

#write.csv(t2,file="SupplementaryTable2.csv",row.names=F,na="")
```

## Supplementary Table 3    
```{r}
t3 <- read_excel("Results Tables.xlsx", sheet = 3, skip = 1)

# models included in this table
mod_list <- list(red_pref,
                 red_pref_male,
                 red_pref_female,
                 green_pref,
                 green_pref_male,
                 green_pref_female,
                 grey_pref,
                 check_pref_male,
                 check_pref_female,
                 orange_pref,
                 orange_pref_male,
                 orange_pref_female)

# position of rows with data in table
pos <- (!is.na(t3$`Repeatability (R)`))

t3$`Repeatability (R)`[pos] <- sapply(mod_list, function(x) round(x$R,3)) %>% unlist 
t3$`95% Confidence Interval`[pos] <- sapply(mod_list, function(x) paste0(round(x$CI_emp[1],3), " - ", round(x$CI_emp[2],3))) %>% unlist

#write.csv(t3,file="SupplementaryTable3.csv",row.names=F,na="")
```


# Figures   
##Tidying Data for Figures
```{r, Wrangling}
rpt_outputs$conditions <- as.factor(rpt_outputs$conditions)

rpt_outputs %<>% mutate(CS = case_when (grepl("Blue_Green", conditions) ~ "Blue/Green",
                                        grepl("Blue_Green", conditions) ~ "Blue/Green",
                                        grepl("Green_Blue", conditions) ~ "Green/Blue",
                                        grepl("Green_Blue", conditions) ~ "Green/Blue",
                                        grepl("First", conditions) ~ "Green/Blue & Blue/Green",
                                        grepl("Second", conditions) ~ "Green/Blue & Blue/Green",
                                        grepl("Third", conditions) ~ "Green/Blue & Blue/Green",
                                        grepl("All", conditions) ~ "Green/Blue & Blue/Green",
                                        grepl("Across", conditions) ~ "Across Conditions"))

rpt_outputs$CS = factor(rpt_outputs$CS, levels = c('Across Conditions','Green/Blue','Blue/Green','Green/Blue & Blue/Green')) #ordering factors correctly for visualisation
rpt_outputs$conditions = factor(rpt_outputs$conditions, levels = c("Across","Green_Blue","Blue_Green", "All", "Third", "Second", "First"))

rpt_outputs %>% slice(1:3) -> new_outputs #remove measurement set data
```

##Figure 2
```{r, Results Figure 2}
pref_cols <- c("Grey" = "#999999","Green" = "#009E73", "Red" = "#D55E00", "Orange" = "#E69F00")

sex_cols1 <- c("male" = "#56B4E9", "female" = "#CC79A7")

fig2A <-  e1 %>% 
  ggplot(aes(sex, difference,  col = sex)) + 
  geom_hline(yintercept = 0, linetype = "dashed", colour = "grey40", size = 0.5) +
  geom_hline(yintercept = 2.695262, colour = "#CC79A7", size = 1.5) +
  geom_hline(yintercept = 5.063168, colour = "#56B4E9", size = 1.5) +
  geom_quasirandom(dodge.width = 0.6, alpha = 0.5) + 
  theme(
    legend.position = c(.95, .95),
    legend.justification = c("right", "top"),
    legend.box.just = "right",
    legend.margin = margin(6, 6, 6, 6)) +
  labs(col = "Sex") +
  labs(x = "Sex", y = "Association Response", title = "Aversive Learning in Zebrafish") +
  scale_color_manual(values = sex_cols1) +
  theme(legend.key = element_rect(fill = "white", colour = "grey90")) +
  theme(axis.text.x = element_text(size = 11))

fig2B <- col_pref %>% 
  ggplot(aes(stim, pref, col = stim)) + 
  geom_hline(yintercept = 30, linetype = "dashed", colour = "grey40", size = 0.5) +
  geom_quasirandom(dodge.width = 0.4, alpha = 0.5) +
  scale_color_manual(values = pref_cols) +
  labs(x = "Colour", y = "Relative Colour Preference", title = "Colour Preference During the Baseline Period") +
  theme(legend.position = "none") +
  scale_x_discrete(name = "Stimulus",labels = c("Grey\nCheck", "Green\nBlue", "Red\nYellow", "Orange\nMagenta")) +
  theme(axis.text.x = element_text(size = 11))

Figure_2 <- ggarrange(fig2A, fig2B,
                    labels = c("A", "B"),
                    ncol = 1, nrow = 2)

Figure_2
```

##Figure 2.1
```{r, Results Figure 2}
#FIGURE IN PROGRESS
##mean lines are wrong
pref_cols <- c("Grey" = "#999999","Green" = "#009E73", "Red" = "#D55E00", "Orange" = "#E69F00")

sex_cols1 <- c("male" = "#CC79A7", "female" = "#56B4E9")

bothexp %<>% mutate(experiment = case_when (grepl("Experiment 1", filepath) ~ "Experiment 1",
                                            grepl("MOBASELINE", filepath) ~ "Experiment 1",
                                           grepl("Experiment 2", filepath) ~ "Experiment 2"))

bothexp$expsex <- as.factor(paste(bothexp$experiment, bothexp$sex, sep = " "))

fig2A.1 <- e1 %>% 
  ggplot(aes(sex, difference,  col = sex)) + 
  geom_hline(yintercept = 0, linetype = "dashed", colour = "grey40", size = 0.5) +
  geom_hline(yintercept = 2.9454, colour = "#CC79A7", size = 1.5) +
  geom_hline(yintercept = 6.0191, colour = "#56B4E9", size = 1.5) +
  geom_quasirandom(dodge.width = 0.6, alpha = 0.5) + 
  theme(
    legend.position = c(.95, .95),
    legend.justification = c("right", "top"),
    legend.box.just = "right",
    legend.margin = margin(6, 6, 6, 6)) +
  labs(col = "Sex") +
  labs(x = "Sex", y = "Association Response", title = "Aversive Learning in Experiment 1") +
  scale_color_manual(values = sex_cols1) +
  theme(legend.key = element_rect(fill = "white", colour = "grey90")) +
  ylim(-22,41) +
  theme(axis.text.x = element_text(size = 11))

fig2B.1 <- e2 %>% 
  ggplot(aes(sex, difference,  col = sex)) + 
  geom_hline(yintercept = 0, linetype = "dashed", colour = "grey40", size = 0.5) +
  geom_hline(yintercept = 6.88287, colour = "#CC79A7", size = 1.5) +
  geom_hline(yintercept = 7.5871, colour = "#56B4E9", size = 1.5) +
  geom_quasirandom(dodge.width = 0.6, alpha = 0.5) + 
  theme(
    legend.position = c(.95, .95),
    legend.justification = c("right", "top"),
    legend.box.just = "right",
    legend.margin = margin(6, 6, 6, 6)) +
  labs(col = "Sex") +
  labs(x = "Sex", y = "Association Response", title = "Aversive Learning in Experiment 2") +
  scale_color_manual(values = sex_cols1) +
  theme(legend.key = element_rect(fill = "white", colour = "grey90")) +
  ylim(-22,41) +
  theme(axis.text.x = element_text(size = 11))

fig2C.1 <- col_pref %>% 
  ggplot(aes(stim, pref, col = stim)) + 
  geom_hline(yintercept = 30, linetype = "dashed", colour = "grey40", size = 0.5) +
  geom_quasirandom(dodge.width = 0.4, alpha = 0.5) +
  scale_color_manual(values = pref_cols) +
  labs(x = "Colour", y = "Relative Colour Preference", title = "Colour Preference During the Baseline Period in Experiment 1") +
  theme(legend.position = "none") +
  scale_x_discrete(name = "Stimulus",labels = c("Grey\nCheck", "Green\nBlue", "Red\nYellow", "Orange\nMagenta")) +
  theme(axis.text.x = element_text(size = 11))

Figure_2.1 <- ggarrange(fig2C.1,
                        ggarrange(fig2A.1, fig2B.1, ncol = 2, labels = c("B", "C")),
                        nrow = 2,
                        labels = "A"
)

Figure_2.1
```


##Figure 3
```{r, Results Figure 3}
##forest plot showing r estimate and 95% CI, conditions grouped according to CS+
new_cols <- c("Across" = "#000000","Green_Blue" = "#009E73", "Blue_Green" = "#56B4E9")

fig3A <- ggplot(data = pref_outputs, aes(x = conditions, y = R, colour = conditions)) +
  geom_errorbar(aes(ymin = lowCI, ymax = highCI), width = 0.15, size = 0.6, position = position_dodge(0.3)) +
  geom_point(aes(x = conditions, y = R), position = position_dodge(0.3), size = 1.5) +
  geom_hline(yintercept = 0, lty = "dotted") +
  labs(x = "Colour", y = "Repeatability (R)", title = "Repeatabiltiy of Colour Preference") +
  facet_col(vars(conditions), scales = "free_y", space = "free") +
  scale_color_manual(values = pref_cols) +
  ylim(0, 0.63) +
  theme(axis.text.y = element_blank(), axis.ticks.y = element_blank()) +
  theme(legend.position = "none") +
  theme(axis.text.x = element_text(size = 11)) +
  theme(strip.text.x = element_text(size = 11)) +
  coord_flip()

fig3B <- ggplot(data = new_outputs, aes(x = conditions, y = R, colour = conditions)) +
  geom_errorbar(aes(ymin = lowCI, ymax = highCI), width = 0.15, size = 0.6, position = position_dodge(0.3)) +
  geom_point(aes(x = conditions, y = R), position = position_dodge(0.3), size = 1.5) +
  geom_hline(yintercept = 0, lty = "dotted") +
  labs(x = "Condition", y = "Repeatability (R)", title = "Repeatabiltiy of Aversive Learning") +
  facet_col(vars(CS), scales = "free_y", space = "free") + #facet_col produces a better forest plot than facet_wrap
  scale_colour_manual(values = new_cols) +
  ylim(0, 0.63) +
  theme(axis.text.y = element_blank(), axis.ticks.y = element_blank()) +
  theme(axis.text.x = element_text(size = 11)) +
  theme(strip.text.x = element_text(size = 11)) +
  theme(legend.position = "none") +
  coord_flip()

Figure_3 <- ggarrange(fig3A, fig3B,
                    labels = c("A", "B"),
                    ncol = 1, nrow = 2,
                    heights = c(1.1,0.8))
Figure_3
```

# Supplementary Figures  

## Supplementary Figure 3 
```{r forest plot with all conditions and sex groupings}
#renaming values to be put in figures
rpt_outputs_all$conditions <- gsub("\\_M", " M", rpt_outputs_all$conditions)
rpt_outputs_all$conditions <- gsub("\\_F", " F", rpt_outputs_all$conditions)
rpt_outputs_all$conditions <- gsub("\\_", " ", rpt_outputs_all$conditions)

rpt_outputs_all[1, 1] <- "Across"
rpt_outputs_all[2, 1] <- "Green/Blue"
rpt_outputs_all[3, 1] <- "Blue/Green"
rpt_outputs_all[4, 1] <- "First"
rpt_outputs_all[5, 1] <- "Second"
rpt_outputs_all[6, 1] <- "Third"
rpt_outputs_all[7, 1] <- "All"
rpt_outputs_all[8, 1] <- "Across Male"
rpt_outputs_all[9, 1] <- "Across Female"
rpt_outputs_all[10, 1] <- "Green/Blue Male"
rpt_outputs_all[11, 1] <- "Green/Blue Female"
rpt_outputs_all[12, 1] <- "Blue/Green Male"
rpt_outputs_all[13, 1] <- "Blue/Green Female"
rpt_outputs_all[14, 1] <- "First Male"
rpt_outputs_all[15, 1] <- "First Female"
rpt_outputs_all[16, 1] <- "Second Male"
rpt_outputs_all[17, 1] <- "Second Female"
rpt_outputs_all[18, 1] <- "Third Male"
rpt_outputs_all[19, 1] <- "Third Female"
rpt_outputs_all[20, 1] <- "All Male"
rpt_outputs_all[21, 1] <- "All Female"

rpt_outputs_all %<>% mutate(Sex = case_when (grepl("Male", conditions) ~ "Male",
                                             grepl("Female", conditions) ~ "Female",
                                             grepl("Green/Blue", conditions) ~ "Mixed",
                                             grepl("Blue/Green", conditions) ~ "Mixed",
                                             grepl("First", conditions) ~ "Mixed",
                                             grepl("Second", conditions) ~ "Mixed",
                                             grepl("Third", conditions) ~ "Mixed",
                                             grepl("All", conditions) ~ "Mixed",
                                             grepl("Across", conditions) ~ "Mixed")) %>% 
                     mutate(CS = case_when (grepl("Blue/", conditions) ~ "Blue",
                                            grepl("Green/", conditions) ~ "Green",
                                            grepl("First", conditions) ~ "Both",
                                            grepl("Second", conditions) ~ "Both",
                                            grepl("Third", conditions) ~ "Both",
                                            grepl("All", conditions) ~ "Both",
                                            grepl("Across", conditions) ~ "All"))

rpt_outputs_all[sapply(rpt_outputs_all, is.character)] <- lapply(rpt_outputs_all[sapply(rpt_outputs_all, is.character)], as.factor) #turning chr to factors

sex_cols <- c("Female" = "#CC79A7","Male" = "#56B4E9", "Mixed" = "#999999")

rpt_outputs_all$CS = factor(rpt_outputs_all$CS, levels = c('All','Green','Blue','Both')) #ordering factors correctly for visualisation

rpt_outputs_all$conditions = factor(rpt_outputs_all$conditions, levels = c("Across","Across Male","Across Female","Green/Blue", "Green/Blue Male", "Green/Blue Female", "Blue/Green", "Blue/Green Male", "Blue/Green Female","First",  "First Male", "First Female", "Second", "Second Male", "Second Female", "Third", "Third Male", "Third Female", "All", "All Male", "All Female"))

##forest plot showing r estimate and 95% CI, conditions grouped according to CS+
Figure_S3 <- ggplot(data = rpt_outputs_all, aes(x = conditions, y = R, colour = Sex)) +
  geom_errorbar(aes(ymin = lowCI, ymax = highCI), width = 0.05, position = position_dodge(0.3)) +
  geom_point(aes(x = conditions, y = R), position = position_dodge(0.3))+
  geom_hline(yintercept = 0, lty = "dotted") +
  labs(x = "Condition", y = "Repeatability (R)") +
  facet_col(vars(CS), scales = "free_y", space = "free") + #facet_col produces a better forest plot than facet_wrap
  scale_colour_manual(values = sex_cols) +
  coord_flip()

Figure_S3
```
Supplementary Figure 4
```{r, Constrast Analysis Plot}
sex_cols <- c("Female" = "#CC79A7","Male" = "#56B4E9", "Mixed" = "#999999")

Figure_S4 <- ggplot(data = df_contrast_learn, aes(x = Distribution, y = R, colour = Sex)) +
  geom_errorbar(aes(ymin = lowCI, ymax = highCI), width = 0.1, position = position_dodge(0.3), size = 1) +
  geom_point(aes(x = Distribution, y = R), position = position_dodge(0.3), size = 3) +
  geom_hline(yintercept = 0, lty = "dotted") +
  labs(x = "Distribution", y = "Repeatability (R)") +
  scale_colour_manual(values = sex_cols) +
  theme(legend.position="none") +
  coord_flip()

Figure_S4
```

## Supplenmetary Figure 5  
```{r}
volt_data %>% filter(test == "CHECK") %>% group_by(test, voltage) %>% summarise(mean = mean(difference), sd = sd(difference), se = sd(difference)/sqrt(n())) -> volt_sum

Figure_S4 <- ggplot(volt_sum, aes(voltage, mean)) +
  geom_bar(position=position_dodge(), stat= "identity", width = 0.7, colour="black") +
  geom_errorbar(aes(ymin=mean - se, ymax = mean + se), width = 0.4, colour = "black", position=position_dodge(0.9)) +
  xlab("Unconditioned Stimulus Voltage") +
  ylab("Association Response (seconds per minute) ± SD") +
  ylim(0,15)
```


## Supplementary Figure 6
```{r}
e1_data %>% filter(zone == "CS") %>% group_by(exp, unit) %>% 
  summarise(mean=mean(time_min), sd=sd(time_min), se=sd(time_min)/sqrt(n())) -> e1_sum
e1_sum %>% group_by(unit) %>% 
  summarise(mean=mean(mean), sd=sd(sd), se=sd(se)/sqrt(n())) -> e1_sum_all

probe_draw_all <- function(dat, title = "") {
  dat <- filter(dat, unit %in% c("PROBE1", "PROBE2", "PROBE3", "PROBE4", "PROBE5"))
  gplot <- ggplot(dat, aes(unit, mean)) +
  geom_bar(position=position_dodge(), stat= "identity", width = 0.7, colour="black") +
  geom_errorbar(aes(ymin=mean - sd, ymax = mean + sd), width = 0.4, colour = "black", position=position_dodge(0.9)) +
  labs(x = "Minute Increments in Probe Period", y = "Time Spent in CS+ During Probe (seconds per minute) ± SD", title = title) +
  ylim(0,45)

  print(gplot)
}

probe_draw_all(e1_sum_all, title =  "All Conditions") -> Figure_S5
```

## Supplementary Figure 7
```{r}
e1_data %>% filter(zone == "CS") %>% group_by(exp, unit) %>% 
  summarise(mean=mean(time_min), sd=sd(time_min), se=sd(time_min)/sqrt(n())) -> e1_sum

probe_draw <- function(dat, condition = "", title = "") {
  dat <- filter(dat, exp == condition)
  dat <- filter(dat, unit %in% c("PROBE1", "PROBE2", "PROBE3", "PROBE4", "PROBE5"))
  gplot <- ggplot(dat, aes(unit, mean)) +
  geom_bar(position=position_dodge(), stat= "identity", width = 0.7, colour="black") +
  geom_errorbar(aes(ymin=mean - se, ymax = mean + se), width = 0.4, colour = "black", position=position_dodge(0.9)) +
  labs(x = "Minute  Increments in Probe Period", y = "CS+ avoidance ± SE", title = title) +
  ylim(0,45)
  
  print(gplot)
}

probe_draw(e1_sum, condition = "REDYEL", title = "Red/Yellow Condition") -> p1
probe_draw(e1_sum, condition = "YELRED", title = "Yellow/Red Condition") -> p2
probe_draw(e1_sum, condition = "GREBLU", title = "Green/Blue Condition") -> p3
probe_draw(e1_sum, condition = "BLUGRE", title = "Blue/Green Condition") -> p4
probe_draw(e1_sum, condition = "CHKGRY", title = "Check/Grey Condition") -> p5
probe_draw(e1_sum, condition = "GRYCHK", title = "Grey/Check Condition") -> p6
probe_draw(e1_sum, condition = "ORAMAG", title = "Orange/Magenta Condition") -> p7
probe_draw(e1_sum, condition = "MAGORA", title = "Magenta/Orange Condition") -> p8


Figure_S6 <- ggarrange(p1, p2, p2, p4, p5, p6, p7, p8,
                    ncol = 2, nrow = 4)

Figure_S6
```

## Supplementary Figure 7
```{r}

```